---
title: "Summary_improved"
output:
  html_document:
    toc: yes
    toc_depth: 4
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(  warning = FALSE,fig.width=15, fig.height=10)

library("psych", lib.loc = "~/R/win-library/3.4")
library("zoom", lib.loc = "~/R/win-library/3.4")
library("knitr", lib.loc = "~/R/win-library/3.4")
```

```{r load data, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

Results_ <-
  read.csv(
    file = "Summary_Benchmarks_.csv",
    header = TRUE,
    sep = ",",
    quote = "\"",
    dec = "."
  )

Results <- Results_[order(Results_[,5]),]
Benchmark_Width <-
  read.csv(
    file = "Summary_Benchmark_Width_Ready.csv",
    header = TRUE,
    sep = ",",
    quote = "\"",
    dec = "."
  )

Instances_SAT <- paste(Benchmark_Width$file_name[Benchmark_Width$sat.unsat=="SATISFIABLE"],".cnf",sep="")
Instances_UNSAT <- paste(Benchmark_Width$file_name[Benchmark_Width$sat.unsat=="UNSATISFIABLE"],".cnf",sep="")


Instances_Primal_Width_0_5 <- paste(Benchmark_Width$file_name[Benchmark_Width$width_primal_s1234>=0 &  Benchmark_Width$width_primal_s1234<=5],".cnf",sep="")
Instances_Primal_Width_6_14 <- paste(Benchmark_Width$file_name[Benchmark_Width$width_primal_s1234>=6 &  Benchmark_Width$width_primal_s1234<=14],".cnf",sep="")
Instances_Primal_Width_15_30 <- paste(Benchmark_Width$file_name[Benchmark_Width$width_primal_s1234>=15 &  Benchmark_Width$width_primal_s1234<=30],".cnf",sep="")

Instances_Incidence_Width_0_5 <- paste(Benchmark_Width$file_name[Benchmark_Width$width_incidence_s1234>=0 &  Benchmark_Width$width_incidence_s1234<=5],".cnf",sep="")
Instances_Incidence_Width_6_14 <- paste(Benchmark_Width$file_name[Benchmark_Width$width_incidence_s1234>=6 &  Benchmark_Width$width_incidence_s1234<=14],".cnf",sep="")
Instances_Incidence_Width_15_30 <- paste(Benchmark_Width$file_name[Benchmark_Width$width_incidence_s1234>=15 &  Benchmark_Width$width_incidence_s1234<=30],".cnf",sep="")
```

# Plots

## gpusat vs gpusat

```{r gpusat vs gpusat, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_ <- Results$time[Results$setting == "primal_double_w-14"]
gpusat2_times_ <- Results$time[Results$setting == "incidence_double_w-14"]

gpusat1_times <- as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric(sort(pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_times <- gpusat_vbest_times[gpusat_vbest_times<900]
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

png(file = "gpusat-incidence_vs_gpusat-primal.png")
# set up the plot
plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

# add lines
lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

# add a title and subtitle
title("primal_double_w-14 vs. incidence_double_w-14")

# add a legend
legend(0, -0.1, xpd=TRUE, c("primal_double_w-14","incidence_double_w-14","best"), cex=0.8, col=c("red","green","blue"), lty="solid", title="solver")
dev.off()

# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_ <- Results$time[Results$setting == "primal_double_w-14"]
gpusat2_times_ <- Results$time[Results$setting == "incidence_double_w-14"]

gpusat1_times <- as.numeric((gpusat1_times_))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric((gpusat2_times_))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric((pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

gpusat1_times <- gpusat1_times[order(gpusat_vbest_times)]
gpusat2_times <- gpusat2_times[order(gpusat_vbest_times)]
gpusat_vbest_times <- gpusat_vbest_times[order(gpusat_vbest_times)]

# set up the plot
plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

# add lines
lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

# add a title and subtitle
title("primal_double_w-14 vs. incidence_double_w-14")

# add a legend
legend(0, -0.1, xpd=TRUE, c("primal_double_w-14","incidence_double_w-14","best"), cex=0.8, col=c("red","green","blue"), lty="solid", title="solver")

```

## gpusat vs. approxmc 

```{r gpusat vs. approxmc, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_ <- Results$time[Results$setting == "primal_double_w-14"]
gpusat2_times_ <- Results$time[Results$solver == "approxmc"]

gpusat1_times <- as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric(sort(pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_times <- gpusat_vbest_times[gpusat_vbest_times<900]
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

# set up the plot
plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

# add lines
lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

# add a title and subtitle
title("primal_double_w-14 vs. approxmc")

# add a legend
legend(0, -0.1, xpd=TRUE, c("primal_double_w-14","approxmc","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_ <- Results$time[Results$solver == "approxmc"]
gpusat2_times_ <- Results$time[Results$setting == "incidence_double_w-14"]

gpusat1_times <- as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric(sort(pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_times <- gpusat_vbest_times[gpusat_vbest_times<900]
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

# set up the plot
plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

# add lines
lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

# add a title and subtitle
title("approxmc vs. incidence_double_w-14")

# add a legend
legend(0, -0.1, xpd=TRUE, c("approxmc","incidence_double_w-14","best"), cex=0.8, col=c("red","green","blue"), lty="solid", title="solver")

# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_ <- Results$time[Results$setting == "primal_double_w-14"]
gpusat2_times_ <- Results$time[Results$solver == "approxmc"]

gpusat1_times <- as.numeric((gpusat1_times_))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric((gpusat2_times_))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric((pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

gpusat1_times <- gpusat1_times[order(gpusat_vbest_times)]
gpusat2_times <- gpusat2_times[order(gpusat_vbest_times)]
gpusat_vbest_times <- gpusat_vbest_times[order(gpusat_vbest_times)]

# set up the plot
plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

# add lines
lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

# add a title and subtitle
title("primal_double_w-14 vs. approxmc")

# add a legend
legend(0, -0.1, xpd=TRUE, c("primal_double_w-14","approxmc","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_ <- Results$time[Results$solver == "approxmc"]
gpusat2_times_ <- Results$time[Results$setting == "incidence_double_w-14"]

gpusat1_times <- as.numeric((gpusat1_times_))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric((gpusat2_times_))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric((pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

gpusat1_times <- gpusat1_times[order(gpusat_vbest_times)]
gpusat2_times <- gpusat2_times[order(gpusat_vbest_times)]
gpusat_vbest_times <- gpusat_vbest_times[order(gpusat_vbest_times)]

# set up the plot
plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

# add lines
lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

# add a title and subtitle
title("approxmc vs. incidence_double_w-14")

# add a legend
legend(0, -0.1, xpd=TRUE, c("approxmc","incidence_double_w-14","best"), cex=0.8, col=c("red","green","blue"), lty="solid", title="solver")

```

## gpusat (vbest) vs. approxmc

```{r gpusat (vbest) vs. approxmc, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_1 <- Results$time[Results$setting == "primal_double_w-14"]
gpusat1_times_2 <- Results$time[Results$setting == "incidence_double_w-14"]
gpusat2_times_ <- Results$time[Results$solver == "approxmc"]

gpusat1_times <- as.numeric(sort(pmin(gpusat1_times_1,gpusat1_times_2)))
gpusat1_times <- gpusat1_times[gpusat1_times < 900]
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric(sort(pmin(gpusat1_times_1,gpusat1_times_2,gpusat2_times_)))
gpusat_vbest_times <- gpusat_vbest_times[gpusat_vbest_times<900]
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

# set up the plot
plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

# add lines
lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

# add a title and subtitle
title("gpusat vs. approxmc")

# add a legend
legend(0, -0.1, xpd=TRUE, c("gpusat","approxmc","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_1 <- Results$time[Results$setting == "primal_double_w-14"]
gpusat1_times_2 <- Results$time[Results$setting == "incidence_double_w-14"]
gpusat2_times_ <- Results$time[Results$solver == "approxmc"]

gpusat1_times <- as.numeric(pmin(gpusat1_times_1,gpusat1_times_2))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric((gpusat2_times_))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric((pmin(gpusat1_times_1,gpusat1_times_2,gpusat2_times_)))
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

gpusat1_times <- gpusat1_times[order(gpusat_vbest_times)]
gpusat2_times <- gpusat2_times[order(gpusat_vbest_times)]
gpusat_vbest_times <- gpusat_vbest_times[order(gpusat_vbest_times)]

# set up the plot
plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

# add lines
lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

# add a title and subtitle
title("gpusat vs. approxmc")

# add a legend
legend(0, -0.1, xpd=TRUE, c("gpusat","approxmc","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

```

## gpusat vs. sharpSAT 

```{r gpusat vs. sharpSAT, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_ <- Results$time[Results$setting == "primal_double_w-14"]
gpusat2_times_ <- Results$time[Results$solver == "sharpSAT"]

gpusat1_times <- as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric(sort(pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_times <- gpusat_vbest_times[gpusat_vbest_times<900]
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

# set up the plot
plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

# add lines
lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

# add a title and subtitle
title("primal_double_w-14 vs. sharpSAT")

# add a legend
legend(0, -0.1, xpd=TRUE, c("primal_double_w-14","sharpSAT","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_ <- Results$time[Results$solver == "sharpSAT"]
gpusat2_times_ <- Results$time[Results$setting == "incidence_double_w-14"]

gpusat1_times <- as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric(sort(pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_times <- gpusat_vbest_times[gpusat_vbest_times<900]
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

# set up the plot
plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

# add lines
lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

# add a title and subtitle
title("sharpSAT vs. incidence_double_w-14")

# add a legend
legend(0, -0.1, xpd=TRUE, c("sharpSAT","incidence_double_w-14","best"), cex=0.8, col=c("red","green","blue"), lty="solid", title="solver")

# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_ <- Results$time[Results$setting == "primal_double_w-14"]
gpusat2_times_ <- Results$time[Results$solver == "sharpSAT"]

gpusat1_times <- as.numeric((gpusat1_times_))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric((gpusat2_times_))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric((pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

gpusat1_times <- gpusat1_times[order(gpusat_vbest_times)]
gpusat2_times <- gpusat2_times[order(gpusat_vbest_times)]
gpusat_vbest_times <- gpusat_vbest_times[order(gpusat_vbest_times)]

# set up the plot
plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

# add lines
lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

# add a title and subtitle
title("primal_double_w-14 vs. sharpSAT")

# add a legend
legend(0, -0.1, xpd=TRUE, c("primal_double_w-14","sharpSAT","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_ <- Results$time[Results$solver == "sharpSAT"]
gpusat2_times_ <- Results$time[Results$setting == "incidence_double_w-14"]

gpusat1_times <- as.numeric((gpusat1_times_))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric((gpusat2_times_))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric((pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

gpusat1_times <- gpusat1_times[order(gpusat_vbest_times)]
gpusat2_times <- gpusat2_times[order(gpusat_vbest_times)]
gpusat_vbest_times <- gpusat_vbest_times[order(gpusat_vbest_times)]

# set up the plot
plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

# add lines
lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

# add a title and subtitle
title("sharpSAT vs. incidence_double_w-14")

# add a legend
legend(0, -0.1, xpd=TRUE, c("sharpSAT","incidence_double_w-14","best"), cex=0.8, col=c("red","green","blue"), lty="solid", title="solver")

```

## gpusat vs. cachet

```{r gpusat vs. cachet, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
### Primal
# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_ <- Results$time[Results$setting == "primal_double_w-14"]
gpusat2_times_ <- Results$time[Results$solver == "cachet"]

gpusat1_times <- as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric(sort(pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_times <- gpusat_vbest_times[gpusat_vbest_times<900]
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

# set up the plot
plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

# add lines
lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

# add a title and subtitle
title("primal_double_w-14 vs. cachet")

# add a legend
legend(0, -0.1, xpd=TRUE, c("primal_double_w-14","cachet","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

### incidence
# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_ <- Results$time[Results$solver == "cachet"]
gpusat2_times_ <- Results$time[Results$setting == "incidence_double_w-14"]

gpusat1_times <- as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric(sort(pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_times <- gpusat_vbest_times[gpusat_vbest_times<900]
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

# set up the plot
plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

# add lines
lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

# add a title and subtitle
title("cachet vs. incidence_double_w-14")

# add a legend
legend(0, -0.1, xpd=TRUE, c("cachet","incidence_double_w-14","best"), cex=0.8, col=c("red","green","blue"), lty="solid", title="solver")


# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_ <- Results$time[Results$setting == "primal_double_w-14"]
gpusat2_times_ <- Results$time[Results$solver == "cachet"]

gpusat1_times <- as.numeric((gpusat1_times_))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric((gpusat2_times_))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric((pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

gpusat1_times <- gpusat1_times[order(gpusat_vbest_times)]
gpusat2_times <- gpusat2_times[order(gpusat_vbest_times)]
gpusat_vbest_times <- gpusat_vbest_times[order(gpusat_vbest_times)]

# set up the plot
plot(range(length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

# add lines
lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

# add a title and subtitle
title("primal_double_w-14 vs. cachet")

# add a legend
legend(0, -0.1, xpd=TRUE, c("primal_double_w-14","cachet","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")


# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_ <- Results$time[Results$solver == "cachet"]
gpusat2_times_ <- Results$time[Results$setting == "incidence_double_w-14"]

gpusat1_times <- as.numeric((gpusat1_times_))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric((gpusat2_times_))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric((pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

gpusat1_times <- gpusat1_times[order(gpusat_vbest_times)]
gpusat2_times <- gpusat2_times[order(gpusat_vbest_times)]
gpusat_vbest_times <- gpusat_vbest_times[order(gpusat_vbest_times)]

# set up the plot
plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

# add lines
lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

# add a title and subtitle
title("cachet vs. incidence_double_w-14")

# add a legend
legend(0, -0.1, xpd=TRUE, c("cachet","incidence_double_w-14","best"), cex=0.8, col=c("red","green","blue"), lty="solid", title="solver")

```

## gpusat vs. dsharp

```{r gpusat vs. dsharp, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_ <- Results$time[Results$setting == "primal_double_w-14"]
gpusat2_times_ <- Results$time[Results$solver == "dsharp"]

gpusat1_times <- as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric(sort(pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_times <- gpusat_vbest_times[gpusat_vbest_times<900]
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

# set up the plot
plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

# add lines
lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

# add a title and subtitle
title("primal_double_w-14 vs. dsharp")

# add a legend
legend(0, -0.1, xpd=TRUE, c("primal_double_w-14","dsharp","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_ <- Results$time[Results$solver == "dsharp"]
gpusat2_times_ <- Results$time[Results$setting == "incidence_double_w-14"]

gpusat1_times <- as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric(sort(pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_times <- gpusat_vbest_times[gpusat_vbest_times<900]
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

# set up the plot
plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

# add lines
lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

# add a title and subtitle
title("dsharp vs. incidence_double_w-14")

# add a legend
legend(0, -0.1, xpd=TRUE, c("dsharp","incidence_double_w-14","best"), cex=0.8, col=c("red","green","blue"), lty="solid", title="solver")

# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_ <- Results$time[Results$setting == "primal_double_w-14"]
gpusat2_times_ <- Results$time[Results$solver == "dsharp"]

gpusat1_times <- as.numeric((gpusat1_times_))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric((gpusat2_times_))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric((pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

gpusat1_times <- gpusat1_times[order(gpusat_vbest_times)]
gpusat2_times <- gpusat2_times[order(gpusat_vbest_times)]
gpusat_vbest_times <- gpusat_vbest_times[order(gpusat_vbest_times)]

# set up the plot
plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

# add lines
lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

# add a title and subtitle
title("primal_double_w-14 vs. dsharp")

# add a legend
legend(0, -0.1, xpd=TRUE, c("primal_double_w-14","dsharp","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_ <- Results$time[Results$solver == "dsharp"]
gpusat2_times_ <- Results$time[Results$setting == "incidence_double_w-14"]

gpusat1_times <- as.numeric((gpusat1_times_))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric((gpusat2_times_))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric((pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

gpusat1_times <- gpusat1_times[order(gpusat_vbest_times)]
gpusat2_times <- gpusat2_times[order(gpusat_vbest_times)]
gpusat_vbest_times <- gpusat_vbest_times[order(gpusat_vbest_times)]

# set up the plot
plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

# add lines
lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

# add a title and subtitle
title("dsharp vs. incidence_double_w-14")

# add a legend
legend(0, -0.1, xpd=TRUE, c("dsharp","incidence_double_w-14","best"), cex=0.8, col=c("red","green","blue"), lty="solid", title="solver")

```

## gpusat vs. sharpSAT vs. cachet vs. dsharp vs. approxmc

```{r gpusat vs. sharpSAT vs. cachet vs. dsharp vs. approxmc, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_ <- Results$time[Results$setting == "primal_double_w-14"]
gpusat2_times_ <- Results$time[Results$setting == "incidence_double_w-14"]
gpusat3_times_ <- Results$time[Results$solver == "sharpSAT"]
gpusat4_times_ <- Results$time[Results$solver == "cachet"]
gpusat5_times_ <- Results$time[Results$solver == "dsharp"]
gpusat6_times_ <- Results$time[Results$solver == "approxmc"]
gpusat7_times_ <- Results$time[Results$solver == "clasp"]
gpusat8_times_ <- Results$time[Results$solver == "lingeling"]
gpusat9_times_ <- Results$time[Results$solver == "minisat"]
gpusat10_times_ <- Results$time[Results$solver == "picosat"]
gpusat11_times_ <- Results$time[Results$solver == "cryptominisat"]

gpusat1_times <- as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))
gpusat3_times <- as.numeric(sort(gpusat3_times_[gpusat3_times_ < 900]))
gpusat3_numbers <- as.numeric(1:length(gpusat3_times))
gpusat4_times <- as.numeric(sort(gpusat4_times_[gpusat4_times_ < 900]))
gpusat4_numbers <- as.numeric(1:length(gpusat4_times))
gpusat5_times <- as.numeric(sort(gpusat5_times_[gpusat5_times_ < 900]))
gpusat5_numbers <- as.numeric(1:length(gpusat5_times))
gpusat6_times <- as.numeric(sort(gpusat6_times_[gpusat6_times_ < 900]))
gpusat6_numbers <- as.numeric(1:length(gpusat6_times))
gpusat7_times <- as.numeric(sort(gpusat7_times_[gpusat7_times_ < 900]))
gpusat7_numbers <- as.numeric(1:length(gpusat7_times))
gpusat8_times <- as.numeric(sort(gpusat8_times_[gpusat8_times_ < 900]))
gpusat8_numbers <- as.numeric(1:length(gpusat8_times))
gpusat9_times <- as.numeric(sort(gpusat9_times_[gpusat9_times_ < 900]))
gpusat9_numbers <- as.numeric(1:length(gpusat9_times))
gpusat10_times <- as.numeric(sort(gpusat10_times_[gpusat10_times_ < 900]))
gpusat10_numbers <- as.numeric(1:length(gpusat10_times))
gpusat11_times <- as.numeric(sort(gpusat11_times_[gpusat11_times_ < 900]))
gpusat11_numbers <- as.numeric(1:length(gpusat11_times))

# set up the plot
plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

# add lines
lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat3_numbers, gpusat3_times, type="l", lwd=0.5, lty="solid", col="yellow", pch=".")
lines(gpusat4_numbers, gpusat4_times, type="l", lwd=0.5, lty="solid", col="violet", pch=".")
lines(gpusat5_numbers, gpusat5_times, type="l", lwd=0.5, lty="solid", col="brown", pch=".")
lines(gpusat6_numbers, gpusat6_times, type="l", lwd=0.5, lty="solid", col="orange", pch=".")
lines(gpusat7_numbers, gpusat7_times, type="l", lwd=0.5, lty="solid", col="gold", pch=".")
lines(gpusat8_numbers, gpusat8_times, type="l", lwd=0.5, lty="solid", col="coral", pch=".")
lines(gpusat9_numbers, gpusat9_times, type="l", lwd=0.5, lty="solid", col="cyan", pch=".")
lines(gpusat10_numbers, gpusat10_times, type="l", lwd=0.5, lty="solid", col="darkgreen", pch=".")
lines(gpusat11_numbers, gpusat11_times, type="l", lwd=0.5, lty="solid", col="darkmagenta", pch=".")

# add a title and subtitle
title("primal_double_w-14 vs. sharpSAT vs. cachet")

# add a legend
legend(0, 900, xpd=TRUE, c("primal_double_w-14","incidence_double_w-14","sharpSAT","cachet","dsharp","approxmc","clasp","lingeling","minisat","picosat","cryptominisat"), cex=0.8, col=c("red","green","yellow","violet","brown","orange","gold","coral","cyan","darkgreen","darkmagenta"), lty="solid", title="solver")

```

## SAT gpusat vs. dynasp

```{r SAT gpusat vs. dynasp kaktus, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
### Primal
gpusat1_times_ <- Results$time[Results$setting == "primal_double_w-14" & Results$instance %in% Instances_SAT]
gpusat2_times_ <- Results$time[Results$setting == "dynasp_primal" & Results$instance %in% Instances_SAT]

gpusat1_times <- as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric(sort(pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_times <- gpusat_vbest_times[gpusat_vbest_times<900]
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

title("gpusat primal vs. dynasp primal")

legend(0, -0.1, xpd=TRUE, c("gpusat","dynasp","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

### incidence
gpusat1_times_ <- Results$time[Results$setting == "incidence_double_w-14" & Results$instance %in% Instances_SAT]
gpusat2_times_ <- Results$time[Results$setting == "dynasp_incidence" & Results$instance %in% Instances_SAT]

gpusat1_times <- as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric(sort(pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_times <- gpusat_vbest_times[gpusat_vbest_times<900]
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

title("gpusat incidence vs. dynasp incidence")

legend(0, -0.1, xpd=TRUE, c("gpusat","dynasp","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

```

```{r SAT gpusat vs. dynasp instance, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
### primal
gpusat1_times_ <- Results$time[Results$setting == "primal_double_w-14" & Results$instance %in% Instances_SAT]
gpusat2_times_ <- Results$time[Results$setting == "dynasp_primal" & Results$instance %in% Instances_SAT]

gpusat1_times <- as.numeric((gpusat1_times_))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric((gpusat2_times_))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric((pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

gpusat1_times <- gpusat1_times[order(gpusat_vbest_times)]
gpusat2_times <- gpusat2_times[order(gpusat_vbest_times)]
gpusat_vbest_times <- gpusat_vbest_times[order(gpusat_vbest_times)]

plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

title("gpusat primal vs. dynasp primal")

legend(0, -0.1, xpd=TRUE, c("gpusat","dynasp","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

### incidende
gpusat1_times_ <- Results$time[Results$setting == "incidence_double_w-14" & Results$instance %in% Instances_SAT]
gpusat2_times_ <- Results$time[Results$setting == "dynasp_incidence" & Results$instance %in% Instances_SAT]

gpusat1_times <- as.numeric((gpusat1_times_))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric((gpusat2_times_))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric((pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

gpusat1_times <- gpusat1_times[order(gpusat_vbest_times)]
gpusat2_times <- gpusat2_times[order(gpusat_vbest_times)]
gpusat_vbest_times <- gpusat_vbest_times[order(gpusat_vbest_times)]

plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

title("gpusat incidence vs. dynasp incidence")

legend(0, -0.1, xpd=TRUE, c("gpusat","dynasp","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

```

## UNSAT gpusat vs. dynasp

```{r UNSAT gpusat vs. dynasp kaktus, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
### Primal
gpusat1_times_ <- Results$time[Results$setting == "primal_double_w-14" & Results$instance %in% Instances_UNSAT]
gpusat2_times_ <- Results$time[Results$setting == "dynasp_primal" & Results$instance %in% Instances_UNSAT]

gpusat1_times <- as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric(sort(pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_times <- gpusat_vbest_times[gpusat_vbest_times<900]
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

title("gpusat primal vs. dynasp primal")

legend(0, -0.1, xpd=TRUE, c("gpusat","dynasp","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

### incidence
gpusat1_times_ <- Results$time[Results$setting == "incidence_double_w-14" & Results$instance %in% Instances_UNSAT]
gpusat2_times_ <- Results$time[Results$setting == "dynasp_incidence" & Results$instance %in% Instances_UNSAT]

gpusat1_times <- as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric(sort(pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_times <- gpusat_vbest_times[gpusat_vbest_times<900]
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

title("gpusat incidence vs. dynasp incidence")

legend(0, -0.1, xpd=TRUE, c("gpusat","dynasp","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

```

```{r UNSAT gpusat vs. dynasp instance, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
### primal
gpusat1_times_ <- Results$time[Results$setting == "primal_double_w-14" & Results$instance %in% Instances_UNSAT]
gpusat2_times_ <- Results$time[Results$setting == "dynasp_primal" & Results$instance %in% Instances_UNSAT]

gpusat1_times <- as.numeric((gpusat1_times_))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric((gpusat2_times_))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric((pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

gpusat1_times <- gpusat1_times[order(gpusat_vbest_times)]
gpusat2_times <- gpusat2_times[order(gpusat_vbest_times)]
gpusat_vbest_times <- gpusat_vbest_times[order(gpusat_vbest_times)]

plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

title("gpusat primal vs. dynasp primal")

legend(0, -0.1, xpd=TRUE, c("gpusat","dynasp","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

### incidende
gpusat1_times_ <- Results$time[Results$setting == "incidence_double_w-14" & Results$instance %in% Instances_UNSAT]
gpusat2_times_ <- Results$time[Results$setting == "dynasp_incidence" & Results$instance %in% Instances_UNSAT]

gpusat1_times <- as.numeric((gpusat1_times_))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric((gpusat2_times_))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric((pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

gpusat1_times <- gpusat1_times[order(gpusat_vbest_times)]
gpusat2_times <- gpusat2_times[order(gpusat_vbest_times)]
gpusat_vbest_times <- gpusat_vbest_times[order(gpusat_vbest_times)]

plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

title("gpusat incidence vs. dynasp incidence")

legend(0, -0.1,  xpd=TRUE, c("gpusat","dynasp","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

```

## gpusat vs. dynasp: Width 0-5

```{r UNSAT gpusat vs. dynasp kaktus Width 0-5, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
### Primal
gpusat1_times_ <- Results$time[Results$setting == "primal_double_w-14" & Results$instance %in% Instances_Primal_Width_0_5]
gpusat2_times_ <- Results$time[Results$setting == "dynasp_primal" & Results$instance %in% Instances_Primal_Width_0_5]

gpusat1_times <- as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric(sort(pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_times <- gpusat_vbest_times[gpusat_vbest_times<900]
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

title("gpusat primal vs. dynasp primal")

legend(0, -0.1, xpd=TRUE, c("gpusat","dynasp","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

### incidence
gpusat1_times_ <- Results$time[Results$setting == "incidence_double_w-14" & Results$instance %in% Instances_Incidence_Width_0_5]
gpusat2_times_ <- Results$time[Results$setting == "dynasp_incidence" & Results$instance %in% Instances_Incidence_Width_0_5]

gpusat1_times <- as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric(sort(pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_times <- gpusat_vbest_times[gpusat_vbest_times<900]
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

title("gpusat incidence vs. dynasp incidence")

legend(0, -0.1, xpd=TRUE, c("gpusat","dynasp","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

```

```{r UNSAT gpusat vs. dynasp instance Width 0-5, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
### primal
gpusat1_times_ <- Results$time[Results$setting == "primal_double_w-14" & Results$instance %in% Instances_Primal_Width_0_5]
gpusat2_times_ <- Results$time[Results$setting == "dynasp_primal" & Results$instance %in% Instances_Primal_Width_0_5]

gpusat1_times <- as.numeric((gpusat1_times_))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric((gpusat2_times_))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric((pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

gpusat1_times <- gpusat1_times[order(gpusat_vbest_times)]
gpusat2_times <- gpusat2_times[order(gpusat_vbest_times)]
gpusat_vbest_times <- gpusat_vbest_times[order(gpusat_vbest_times)]

plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

title("gpusat primal vs. dynasp primal")

legend(0, -0.1, xpd=TRUE, c("gpusat","dynasp","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

### incidende
gpusat1_times_ <- Results$time[Results$setting == "incidence_double_w-14" & Results$instance %in% Instances_Incidence_Width_0_5]
gpusat2_times_ <- Results$time[Results$setting == "dynasp_incidence" & Results$instance %in% Instances_Incidence_Width_0_5]

gpusat1_times <- as.numeric((gpusat1_times_))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric((gpusat2_times_))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric((pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

gpusat1_times <- gpusat1_times[order(gpusat_vbest_times)]
gpusat2_times <- gpusat2_times[order(gpusat_vbest_times)]
gpusat_vbest_times <- gpusat_vbest_times[order(gpusat_vbest_times)]

plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

title("gpusat incidence vs. dynasp incidence")

legend(0, -0.1,  xpd=TRUE, c("gpusat","dynasp","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

```

## gpusat vs. dynasp: Width 6-14

```{r UNSAT gpusat vs. dynasp kaktus Width 6-14, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
### Primal
gpusat1_times_ <- Results$time[Results$setting == "primal_double_w-14" & Results$instance %in% Instances_Primal_Width_6_14]
gpusat2_times_ <- Results$time[Results$setting == "dynasp_primal" & Results$instance %in% Instances_Primal_Width_6_14]

gpusat1_times <- as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric(sort(pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_times <- gpusat_vbest_times[gpusat_vbest_times<900]
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

title("gpusat primal vs. dynasp primal")

legend(0, -0.1, xpd=TRUE, c("gpusat","dynasp","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

### incidence
gpusat1_times_ <- Results$time[Results$setting == "incidence_double_w-14" & Results$instance %in% Instances_Incidence_Width_6_14]
gpusat2_times_ <- Results$time[Results$setting == "dynasp_incidence" & Results$instance %in% Instances_Incidence_Width_6_14]

gpusat1_times <- as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric(sort(pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_times <- gpusat_vbest_times[gpusat_vbest_times<900]
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

title("gpusat incidence vs. dynasp incidence")

legend(0, -0.1, xpd=TRUE, c("gpusat","dynasp","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

```

```{r UNSAT gpusat vs. dynasp instance Width 6-14, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
### primal
gpusat1_times_ <- Results$time[Results$setting == "primal_double_w-14" & Results$instance %in% Instances_Primal_Width_6_14]
gpusat2_times_ <- Results$time[Results$setting == "dynasp_primal" & Results$instance %in% Instances_Primal_Width_6_14]

gpusat1_times <- as.numeric((gpusat1_times_))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric((gpusat2_times_))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric((pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

gpusat1_times <- gpusat1_times[order(gpusat_vbest_times)]
gpusat2_times <- gpusat2_times[order(gpusat_vbest_times)]
gpusat_vbest_times <- gpusat_vbest_times[order(gpusat_vbest_times)]

plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

title("gpusat primal vs. dynasp primal")

legend(0, -0.1, xpd=TRUE, c("gpusat","dynasp","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

### incidende
gpusat1_times_ <- Results$time[Results$setting == "incidence_double_w-14" & Results$instance %in% Instances_Incidence_Width_6_14]
gpusat2_times_ <- Results$time[Results$setting == "dynasp_incidence" & Results$instance %in% Instances_Incidence_Width_6_14]

gpusat1_times <- as.numeric((gpusat1_times_))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric((gpusat2_times_))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric((pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

gpusat1_times <- gpusat1_times[order(gpusat_vbest_times)]
gpusat2_times <- gpusat2_times[order(gpusat_vbest_times)]
gpusat_vbest_times <- gpusat_vbest_times[order(gpusat_vbest_times)]

plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

title("gpusat incidence vs. dynasp incidence")

legend(0, -0.1,  xpd=TRUE, c("gpusat","dynasp","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

```

## gpusat vs. dynasp: Width 15-30

```{r UNSAT gpusat vs. dynasp kaktus Width 15-30, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
### Primal
gpusat1_times_ <- Results$time[Results$setting == "primal_double_w-14" & Results$instance %in% Instances_Primal_Width_15_30]
gpusat2_times_ <- Results$time[Results$setting == "dynasp_primal" & Results$instance %in% Instances_Primal_Width_15_30]

gpusat1_times <- as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric(sort(pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_times <- gpusat_vbest_times[gpusat_vbest_times<900]
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

title("gpusat primal vs. dynasp primal")

legend(0, -0.1, xpd=TRUE, c("gpusat","dynasp","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

### incidence
gpusat1_times_ <- Results$time[Results$setting == "incidence_double_w-14" & Results$instance %in% Instances_Incidence_Width_15_30]
gpusat2_times_ <- Results$time[Results$setting == "dynasp_incidence" & Results$instance %in% Instances_Incidence_Width_15_30]

gpusat1_times <- as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric(sort(pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_times <- gpusat_vbest_times[gpusat_vbest_times<900]
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

title("gpusat incidence vs. dynasp incidence")

legend(0, -0.1, xpd=TRUE, c("gpusat","dynasp","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

```

```{r UNSAT gpusat vs. dynasp instance Width 15-30, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
### primal
gpusat1_times_ <- Results$time[Results$setting == "primal_double_w-14" & Results$instance %in% Instances_Primal_Width_15_30]
gpusat2_times_ <- Results$time[Results$setting == "dynasp_primal" & Results$instance %in% Instances_Primal_Width_15_30]

gpusat1_times <- as.numeric((gpusat1_times_))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric((gpusat2_times_))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric((pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

gpusat1_times <- gpusat1_times[order(gpusat_vbest_times)]
gpusat2_times <- gpusat2_times[order(gpusat_vbest_times)]
gpusat_vbest_times <- gpusat_vbest_times[order(gpusat_vbest_times)]

plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

title("gpusat primal vs. dynasp primal")

legend(0, -0.1, xpd=TRUE, c("gpusat","dynasp","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

### incidende
gpusat1_times_ <- Results$time[Results$setting == "incidence_double_w-14" & Results$instance %in% Instances_Incidence_Width_15_30]
gpusat2_times_ <- Results$time[Results$setting == "dynasp_incidence" & Results$instance %in% Instances_Incidence_Width_15_30]

gpusat1_times <- as.numeric((gpusat1_times_))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric((gpusat2_times_))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric((pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

gpusat1_times <- gpusat1_times[order(gpusat_vbest_times)]
gpusat2_times <- gpusat2_times[order(gpusat_vbest_times)]
gpusat_vbest_times <- gpusat_vbest_times[order(gpusat_vbest_times)]

plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

title("gpusat incidence vs. dynasp incidence")

legend(0, -0.1,  xpd=TRUE, c("gpusat","dynasp","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

```

## dynasp vs. sharpsat

```{r dynasp vs. sharpSAT, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_ <- Results$time[Results$setting == "dynasp_primal"]
gpusat2_times_ <- Results$time[Results$solver == "sharpSAT"]

gpusat1_times <- as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric(sort(pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_times <- gpusat_vbest_times[gpusat_vbest_times<900]
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

# set up the plot
plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

# add lines
lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

# add a title and subtitle
title("dynasp_primal vs. sharpSAT")

# add a legend
legend(0, -0.1, xpd=TRUE, c("dynasp_primal","sharpSAT","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_ <- Results$time[Results$solver == "sharpSAT"]
gpusat2_times_ <- Results$time[Results$setting == "dynasp_incidence"]

gpusat1_times <- as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric(sort(pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_times <- gpusat_vbest_times[gpusat_vbest_times<900]
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

# set up the plot
plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

# add lines
lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

# add a title and subtitle
title("sharpSAT vs. dynasp_incidence")

# add a legend
legend(0, -0.1, xpd=TRUE, c("sharpSAT","dynasp_incidence","best"), cex=0.8, col=c("red","green","blue"), lty="solid", title="solver")

# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_ <- Results$time[Results$setting == "dynasp_primal"]
gpusat2_times_ <- Results$time[Results$solver == "sharpSAT"]

gpusat1_times <- as.numeric((gpusat1_times_))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric((gpusat2_times_))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric((pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

gpusat1_times <- gpusat1_times[order(gpusat_vbest_times)]
gpusat2_times <- gpusat2_times[order(gpusat_vbest_times)]
gpusat_vbest_times <- gpusat_vbest_times[order(gpusat_vbest_times)]

# set up the plot
plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

# add lines
lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

# add a title and subtitle
title("dynasp_primal vs. sharpSAT")

# add a legend
legend(0, -0.1, xpd=TRUE, c("dynasp_primal","sharpSAT","best"), cex=0.8, col=c("green","red","blue"), lty="solid", title="solver")

# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_ <- Results$time[Results$solver == "sharpSAT"]
gpusat2_times_ <- Results$time[Results$setting == "dynasp_incidence"]

gpusat1_times <- as.numeric((gpusat1_times_))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric((gpusat2_times_))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <- as.numeric((pmin(gpusat1_times_,gpusat2_times_)))
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

gpusat1_times <- gpusat1_times[order(gpusat_vbest_times)]
gpusat2_times <- gpusat2_times[order(gpusat_vbest_times)]
gpusat_vbest_times <- gpusat_vbest_times[order(gpusat_vbest_times)]

# set up the plot
plot(range(0:length(gpusat_vbest_times)+1), range(0:max(gpusat1_times,gpusat2_times)), type="n", xlab="Instances",   ylab="Time", lab=c(20,10,7))

# add lines
lines(gpusat1_numbers, gpusat1_times, type="l", lwd=0.5, lty="solid", col="red", pch=".")
lines(gpusat2_numbers, gpusat2_times, type="l", lwd=0.5, lty="solid", col="green", pch=".")
lines(gpusat_vbest_numbers, gpusat_vbest_times, type="l", lwd=0.5, lty="solid", col="blue", pch=".")

# add a title and subtitle
title("sharpSAT vs. dynasp_incidence")

# add a legend
legend(0, -0.1, xpd=TRUE, c("sharpSAT","dynasp_incidence","best"), cex=0.8, col=c("red","green","blue"), lty="solid", title="solver")

```

## gpusat vs. dynasp: Solutions more than 5000

## gpusat vs. dynasp: Solutions less than 5000
