---
title: "Summary"
output:
  html_document:
    toc: yes
    toc_depth: 4
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE,
                      fig.width = 20,
                      fig.height = 10)

library("psych", lib.loc = "~/R/win-library/3.4")
library("zoom", lib.loc = "~/R/win-library/3.4")
library("knitr", lib.loc = "~/R/win-library/3.4")

```

```{r load data, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
PlotSize <- 800
Results_ <-
  read.csv(
    file = "Summary_Benchmarks.csv",
    header = TRUE,
    sep = ",",
    quote = "\"",
    dec = "."
  )

Results_improved_ <-
  read.csv(
    file = "Summary_Benchmarks_improved.csv",
    header = TRUE,
    sep = ",",
    quote = "\"",
    dec = "."
  )


Results <- Results_[order(Results_[, 5]), ]
Results_improved <-
  Results_improved_[order(Results_improved_[, 5]), ]

Benchmark_Width <-
  read.csv(
    file = "Summary_Benchmark_Width_Ready.csv",
    header = TRUE,
    sep = ",",
    quote = "\"",
    dec = "."
  )

Benchmark_Width$X.models.sharpSAT <-
  as.numeric(Benchmark_Width$X.models.sharpSAT)

Instances_SAT <-
  paste(Benchmark_Width$file_name[Benchmark_Width$sat.unsat == "SATISFIABLE"], ".cnf", sep =
          "")
Instances_UNSAT <-
  paste(Benchmark_Width$file_name[Benchmark_Width$sat.unsat == "UNSATISFIABLE"], ".cnf", sep =
          "")

Instances_Primal_Width_0_20 <-
  paste(Benchmark_Width$file_name[Benchmark_Width$width_primal_s1234 >= 0 &
                                    Benchmark_Width$width_primal_s1234 <= 20], ".cnf", sep = "")
Instances_Primal_Width_1_15 <-
  paste(Benchmark_Width$file_name[Benchmark_Width$width_primal_s1234 >= 1 &
                                    Benchmark_Width$width_primal_s1234 <= 15], ".cnf", sep = "")
Instances_Primal_Width_16_20 <-
  paste(Benchmark_Width$file_name[Benchmark_Width$width_primal_s1234 >= 16 &
                                    Benchmark_Width$width_primal_s1234 <= 20], ".cnf", sep = "")
Instances_Primal_Width_21_25 <-
  paste(Benchmark_Width$file_name[Benchmark_Width$width_primal_s1234 >= 21 &
                                    Benchmark_Width$width_primal_s1234 <= 25], ".cnf", sep = "")
Instances_Primal_Width_26_30 <-
  paste(Benchmark_Width$file_name[Benchmark_Width$width_primal_s1234 >= 26 &
                                    Benchmark_Width$width_primal_s1234 <= 30], ".cnf", sep = "")
Instances_Primal_Width_31_40 <-
  paste(Benchmark_Width$file_name[Benchmark_Width$width_primal_s1234 >= 31 &
                                    Benchmark_Width$width_primal_s1234 <= 40], ".cnf", sep = "")
Instances_Primal_Width_30 <-
  paste(Benchmark_Width$file_name[Benchmark_Width$width_primal_s1234 <= 30], ".cnf", sep = "")


Instances_Incidence_Width_0_20 <-
  paste(Benchmark_Width$file_name[Benchmark_Width$width_incidence_s1234 >= 0 &
                                    Benchmark_Width$width_incidence_s1234 <= 20], ".cnf", sep = "")
Instances_Incidence_Width_1_15 <-
  paste(Benchmark_Width$file_name[Benchmark_Width$width_incidence_s1234 >= 1 &
                                    Benchmark_Width$width_incidence_s1234 <= 15], ".cnf", sep = "")
Instances_Incidence_Width_16_20 <-
  paste(Benchmark_Width$file_name[Benchmark_Width$width_incidence_s1234 >= 16 &
                                    Benchmark_Width$width_incidence_s1234 <= 20], ".cnf", sep = "")
Instances_Incidence_Width_21_25 <-
  paste(Benchmark_Width$file_name[Benchmark_Width$width_incidence_s1234 >= 21 &
                                    Benchmark_Width$width_incidence_s1234 <= 25], ".cnf", sep = "")
Instances_Incidence_Width_26_30 <-
  paste(Benchmark_Width$file_name[Benchmark_Width$width_incidence_s1234 >= 26 &
                                    Benchmark_Width$width_incidence_s1234 <= 30], ".cnf", sep = "")
Instances_Incidence_Width_31_40 <-
  paste(Benchmark_Width$file_name[Benchmark_Width$width_incidence_s1234 >= 31 &
                                    Benchmark_Width$width_incidence_s1234 <= 40], ".cnf", sep = "")
Instances_Incidence_Width_30 <-
  paste(Benchmark_Width$file_name[Benchmark_Width$width_incidence_s1234 <= 30], ".cnf", sep = "")



Instances_Models_5000 <-
  paste(Benchmark_Width$file_name[Benchmark_Width$X.models.sharpSAT <= 5000], ".cnf", sep = "")

Instances_Models_5000_p <-
  paste(Benchmark_Width$file_name[Benchmark_Width$X.models.sharpSAT > 5000], ".cnf", sep = "")

```

```{r plot functions 2, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# create kaktus plot
generateKaktusPlot <-
  function(PlotTitle,
           Instances1,
           Instances2,
           name,
           name1,
           name2) {
    gpusat1_times_ <- Results$time[Instances1]
    gpusat2_times_ <- Results$time[Instances2]
    
    gpusat1_times <-      as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
    gpusat1_numbers <-      if (length(gpusat1_times) > 0)        as.numeric(1:length(gpusat1_times))    else      c()
    gpusat2_times <-      as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
    gpusat2_numbers <-      if (length(gpusat2_times) > 0)        as.numeric(1:length(gpusat2_times))    else      c()
    
    cat(sprintf("%s: %d\n", name1, length(gpusat1_times)))
    cat(sprintf("%s: %d\n", name2, length(gpusat2_times)))
    
    gpusat_vbest_times <-      as.numeric(sort(pmin(gpusat1_times_, gpusat2_times_)))
    gpusat_vbest_times <-      gpusat_vbest_times[gpusat_vbest_times < 900]
    gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))
    
    plot(
      range(0:length(gpusat_vbest_times) + 1),
      range(0:max(gpusat1_times, gpusat2_times)),
      type = "n",
      xlab = "Instances",
      ylab = "Time",
      lab = c(20, 10, 7)
    )
    lines(
      gpusat1_numbers,
      gpusat1_times,
      type = "l",
      lwd = 0.5,
      lty = "solid",
      col = "green",
      pch = "."
    )
    lines(
      gpusat2_numbers,
      gpusat2_times,
      type = "l",
      lwd = 0.5,
      lty = "solid",
      col = "red",
      pch = "."
    )
    lines(
      gpusat_vbest_numbers,
      gpusat_vbest_times,
      type = "l",
      lwd = 0.5,
      lty = "solid",
      col = "blue",
      pch = "."
    )
    title(PlotTitle)
    legend(
      0,
      max(gpusat1_times, gpusat2_times),
      xpd = TRUE,
      c(name1, name2, "best"),
      cex = 0.8,
      col = c("green", "red", "blue"),
      lty = "solid",
      title = "solver"
    )
  }

# create instance plot
generateInstancePlot <-
  function(PlotTitle,
           Instances1,
           Instances2,
           name,
           name1,
           name2) {
    gpusat1_times_ <- Results$time[Instances1]
    gpusat2_times_ <- Results$time[Instances2]
    
    gpusat1_times <- as.numeric((gpusat1_times_))
    gpusat1_numbers <-      if (length(gpusat1_times) > 0)        as.numeric(1:length(gpusat1_times))    else      c()
    gpusat2_times <- as.numeric((gpusat2_times_))
    gpusat2_numbers <-      if (length(gpusat2_times) > 0)        as.numeric(1:length(gpusat2_times))    else      c()
    
    gpusat_vbest_times <-      as.numeric((pmin(gpusat1_times_, gpusat2_times_)))
    gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))
    
    gpusat1_times <- gpusat1_times[order(gpusat_vbest_times)]
    gpusat2_times <- gpusat2_times[order(gpusat_vbest_times)]
    gpusat_vbest_times <-      gpusat_vbest_times[order(gpusat_vbest_times)]
    
    plot(
      range(0:length(gpusat_vbest_times) + 1),
      range(0:max(gpusat1_times, gpusat2_times)),
      type = "n",
      xlab = "Instances",
      ylab = "Time",
      lab = c(20, 10, 7)
    )
    lines(
      gpusat1_numbers,
      gpusat1_times,
      type = "l",
      lwd = 0.5,
      lty = "solid",
      col = "green",
      pch = "."
    )
    lines(
      gpusat2_numbers,
      gpusat2_times,
      type = "l",
      lwd = 0.5,
      lty = "solid",
      col = "red",
      pch = "."
    )
    lines(
      gpusat_vbest_numbers,
      gpusat_vbest_times,
      type = "l",
      lwd = 0.5,
      lty = "solid",
      col = "blue",
      pch = "."
    )
    title(PlotTitle)
    legend(
      0,
      max(gpusat1_times, gpusat2_times),
      xpd = TRUE,
      c(name1, name2, "best"),
      cex = 0.8,
      col = c("green", "red", "blue"),
      lty = "solid",
      title = "solver"
    )
  }

generateInstanceKaktusPlot <-
  function(PlotTitle,
           Instances1,
           Instances2,
           name,
           name1,
           name2) {
    generateKaktusPlot(
      paste("kaktus ", PlotTitle, sep = ""),
      Instances1,
      Instances2,
      paste("./Plots/kaktus_", name, sep = ""),
      name1,
      name2
    )
    generateInstancePlot(
      paste("instance ", PlotTitle, sep = ""),
      Instances1,
      Instances2,
      paste("./Plots/instance_", name, sep = ""),
      name1,
      name2
    )
  }


```

```{r plot functions 4, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# create kaktus plot
generateKaktusPlot4 <-
  function(PlotTitle,
           Instances1,
           Instances2,
           Instances3,
           Instances4,
           name,
           name1,
           name2,
           name3,
           name4) {
    gpusat1_times_ <- Results$time[Instances1]
    gpusat2_times_ <- Results$time[Instances2]
    gpusat3_times_ <- Results$time[Instances3]
    gpusat4_times_ <- Results$time[Instances4]
    
    gpusat1_times <-      as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
    gpusat1_numbers <-      if (length(gpusat1_times) > 0)        as.numeric(1:length(gpusat1_times))    else      c()
    gpusat2_times <-      as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
    gpusat2_numbers <-      if (length(gpusat2_times) > 0)        as.numeric(1:length(gpusat2_times))    else      c()
    gpusat3_times <-      as.numeric(sort(gpusat3_times_[gpusat3_times_ < 900]))
    gpusat3_numbers <-      if (length(gpusat3_times) > 0)        as.numeric(1:length(gpusat3_times))    else      c()
    gpusat4_times <-      as.numeric(sort(gpusat4_times_[gpusat4_times_ < 900]))
    gpusat4_numbers <-      if (length(gpusat4_times) > 0)        as.numeric(1:length(gpusat4_times))    else      c()
    
    cat(sprintf("%s: %d\n", name1, length(gpusat1_times)))
    cat(sprintf("%s: %d\n", name2, length(gpusat2_times)))
    cat(sprintf("%s: %d\n", name3, length(gpusat3_times)))
    cat(sprintf("%s: %d\n", name4, length(gpusat4_times)))
    
    gpusat_vbest_times <-
      as.numeric(sort(
        pmin(
          gpusat1_times_,
          gpusat2_times_,
          gpusat3_times_,
          gpusat4_times_
        )
      ))
    gpusat_vbest_times <-
      gpusat_vbest_times[gpusat_vbest_times < 900]
    gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))
    
    plot(
      range(0:length(gpusat_vbest_times) + 1),
      range(
        0:max(gpusat1_times, gpusat2_times, gpusat3_times, gpusat4_times)
      ),
      type = "n",
      xlab = "Instances",
      ylab = "Time",
      lab = c(20, 10, 7)
    )
    lines(
      gpusat1_numbers,
      gpusat1_times,
      type = "l",
      lwd = 0.5,
      lty = "solid",
      col = "green",
      pch = "."
    )
    lines(
      gpusat2_numbers,
      gpusat2_times,
      type = "l",
      lwd = 0.5,
      lty = "solid",
      col = "red",
      pch = "."
    )
    lines(
      gpusat3_numbers,
      gpusat3_times,
      type = "l",
      lwd = 0.5,
      lty = "solid",
      col = "cyan",
      pch = "."
    )
    lines(
      gpusat4_numbers,
      gpusat4_times,
      type = "l",
      lwd = 0.5,
      lty = "solid",
      col = "violet",
      pch = "."
    )
    lines(
      gpusat_vbest_numbers,
      gpusat_vbest_times,
      type = "l",
      lwd = 0.5,
      lty = "solid",
      col = "blue",
      pch = "."
    )
    title(PlotTitle)
    legend(
      0,
      max(gpusat1_times, gpusat2_times, gpusat3_times, gpusat4_times),
      xpd = TRUE,
      c(name1, name2, name3, name4, "best"),
      cex = 0.8,
      col = c("green", "red", "cyan", "violet", "blue"),
      lty = "solid",
      title = "solver"
    )
  }

# create instance plot
generateInstancePlot4 <-
  function(PlotTitle,
           Instances1,
           Instances2,
           Instances3,
           Instances4,
           name,
           name1,
           name2,
           name3,
           name4) {
    gpusat1_times_ <- Results$time[Instances1]
    gpusat2_times_ <- Results$time[Instances2]
    gpusat3_times_ <- Results$time[Instances3]
    gpusat4_times_ <- Results$time[Instances4]
    
    gpusat1_times <- as.numeric((gpusat1_times_))
    gpusat1_numbers <-      if (length(gpusat1_times) > 0)        as.numeric(1:length(gpusat1_times))    else      c()
    gpusat2_times <- as.numeric((gpusat2_times_))
    gpusat2_numbers <-      if (length(gpusat2_times) > 0)        as.numeric(1:length(gpusat2_times))    else      c()
    gpusat3_times <- as.numeric((gpusat3_times_))
    gpusat3_numbers <-      if (length(gpusat3_times) > 0)        as.numeric(1:length(gpusat3_times))    else      c()
    gpusat4_times <- as.numeric((gpusat4_times_))
    gpusat4_numbers <-      if (length(gpusat4_times) > 0)        as.numeric(1:length(gpusat4_times))    else      c()
    
    gpusat_vbest_times <-
      as.numeric((
        pmin(
          gpusat1_times_,
          gpusat2_times_,
          gpusat3_times_,
          gpusat4_times_
        )
      ))
    gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))
    
    gpusat1_times <- gpusat1_times[order(gpusat_vbest_times)]
    gpusat2_times <- gpusat2_times[order(gpusat_vbest_times)]
    gpusat3_times <- gpusat3_times[order(gpusat_vbest_times)]
    gpusat4_times <- gpusat4_times[order(gpusat_vbest_times)]
    gpusat_vbest_times <-      gpusat_vbest_times[order(gpusat_vbest_times)]
    
    plot(
      range(0:length(gpusat_vbest_times) + 1),
      range(
        0:max(gpusat1_times, gpusat2_times, gpusat3_times, gpusat4_times)
      ),
      type = "n",
      xlab = "Instances",
      ylab = "Time",
      lab = c(20, 10, 7)
    )
    lines(
      gpusat1_numbers,
      gpusat1_times,
      type = "l",
      lwd = 0.5,
      lty = "solid",
      col = "green",
      pch = "."
    )
    lines(
      gpusat2_numbers,
      gpusat2_times,
      type = "l",
      lwd = 0.5,
      lty = "solid",
      col = "red",
      pch = "."
    )
    lines(
      gpusat3_numbers,
      gpusat3_times,
      type = "l",
      lwd = 0.5,
      lty = "solid",
      col = "cyan",
      pch = "."
    )
    lines(
      gpusat4_numbers,
      gpusat4_times,
      type = "l",
      lwd = 0.5,
      lty = "solid",
      col = "violet",
      pch = "."
    )
    lines(
      gpusat_vbest_numbers,
      gpusat_vbest_times,
      type = "l",
      lwd = 0.5,
      lty = "solid",
      col = "blue",
      pch = "."
    )
    title(PlotTitle)
    legend(
      0,
      max(gpusat1_times, gpusat2_times, gpusat3_times, gpusat4_times),
      xpd = TRUE,
      c(name1, name2, name3, name4, "best"),
      cex = 0.8,
      col = c("green", "red", "cyan", "violet", "blue"),
      lty = "solid",
      title = "solver"
    )
  }

generateInstanceKaktusPlot4 <-
  function(PlotTitle,
           Instances1,
           Instances2,
           Instances3,
           Instances4,
           name,
           name1,
           name2,
           name3,
           name4) {
    generateKaktusPlot4(
      paste("kaktus ", PlotTitle, sep = ""),
      Instances1,
      Instances2,
      Instances3,
      Instances4,
      paste("./Plots/kaktus_", name, sep = ""),
      name1,
      name2,
      name3,
      name4
    )
    generateInstancePlot4(
      paste("instance ", PlotTitle, sep = ""),
      Instances1,
      Instances2,
      Instances3,
      Instances4,
      paste("./Plots/instance_", name, sep = ""),
      name1,
      name2,
      name3,
      name4
    )
  }

```

# Plots

## gpusat normal vs gpusat improvement

```{r gpusat vs gpusat kaktus, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
PlotTitle <- "gpusat normal vs. improvement"
Instances1 <- Results$setting == "primal_double_w-14_m-24"
Instances2 <- Results$setting == "incidence_double_w-14_m-24"
Instances3 <- Results_improved$setting == "primal_double_w-14_m-24"
Instances4 <- Results_improved$setting == "incidence_double_w-14_m-24"
name <- "gpusat_incidence_vs_primal.png"
name1 <- "primal"
name2 <- "incidence"
name3 <- "primal_improvement"
name4 <- "incidence_improvement"

gpusat1_times_ <- Results$time[Instances1]
gpusat2_times_ <- Results$time[Instances2]
gpusat3_times_ <- Results_improved$time[Instances3]
gpusat4_times_ <- Results_improved$time[Instances4]

gpusat1_times <-  as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
gpusat1_numbers <-  if (length(gpusat1_times) > 0) as.numeric(1:length(gpusat1_times)) else c()
gpusat2_times <-  as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <-  if (length(gpusat2_times) > 0)    as.numeric(1:length(gpusat2_times)) else c()
gpusat3_times <-  as.numeric(sort(gpusat3_times_[gpusat3_times_ < 900]))
gpusat3_numbers <-  if (length(gpusat3_times) > 0)    as.numeric(1:length(gpusat3_times))else  c()
gpusat4_times <-  as.numeric(sort(gpusat4_times_[gpusat4_times_ < 900]))
gpusat4_numbers <-  if (length(gpusat4_times) > 0)    as.numeric(1:length(gpusat4_times))else  c()

cat(sprintf("%s: %d\n", name1, length(gpusat1_times)))
cat(sprintf("%s: %d\n", name2, length(gpusat2_times)))
cat(sprintf("%s: %d\n", name3, length(gpusat3_times)))
cat(sprintf("%s: %d\n", name4, length(gpusat4_times)))

gpusat_vbest_times <-
  as.numeric(sort(
    pmin(
      gpusat1_times_,
      gpusat2_times_,
      gpusat3_times_,
      gpusat4_times_
    )
  ))
gpusat_vbest_times <- gpusat_vbest_times[gpusat_vbest_times < 900]
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

plot(
  range(0:length(gpusat_vbest_times) + 1),
  range(
    0:max(gpusat1_times, gpusat2_times, gpusat3_times, gpusat4_times)
  ),
  type = "n",
  xlab = "Instances",
  ylab = "Time",
  lab = c(20, 10, 7)
)
lines(
  gpusat1_numbers,
  gpusat1_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "green",
  pch = "."
)
lines(
  gpusat2_numbers,
  gpusat2_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "red",
  pch = "."
)
lines(
  gpusat3_numbers,
  gpusat3_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "cyan",
  pch = "."
)
lines(
  gpusat4_numbers,
  gpusat4_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "violet",
  pch = "."
)
lines(
  gpusat_vbest_numbers,
  gpusat_vbest_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "blue",
  pch = "."
)
title(PlotTitle)
legend(
  0,
  0,
  xpd = TRUE,
  c(name1, name2, name3, name4, "best"),
  cex = 0.8,
  col = c("green", "red", "cyan", "violet", "blue"),
  lty = "solid",
  title = "solver"
)

```

```{r gpusat vs gpusat instance, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
PlotTitle <- "gpusat normal vs. improvement"
name <- "gpusat_incidence_vs_primal.png"
name1 <- "primal"
name2 <- "incidence"
name3 <- "primal_improvement"
name4 <- "incidence_improvement"

gpusat1_times_ <-  Results$time[Results$setting == "primal_double_w-14_m-24"]
gpusat2_times_ <-  Results$time[Results$setting == "incidence_double_w-14_m-24"]
gpusat3_times_ <-  Results_improved$time[Results_improved$setting == "primal_double_w-14_m-24"]
gpusat4_times_ <-  Results_improved$time[Results_improved$setting == "incidence_double_w-14_m-24"]

gpusat1_times <- as.numeric(gpusat1_times_)
gpusat1_numbers <-  if (length(gpusat1_times) > 0)    as.numeric(1:length(gpusat1_times))else  c()
gpusat2_times <- as.numeric(gpusat2_times_)
gpusat2_numbers <-  if (length(gpusat2_times) > 0)    as.numeric(1:length(gpusat2_times))else  c()
gpusat3_times <- as.numeric(gpusat3_times_)
gpusat3_numbers <-  if (length(gpusat3_times) > 0)    as.numeric(1:length(gpusat3_times))else  c()
gpusat4_times <- as.numeric(gpusat4_times_)
gpusat4_numbers <-  if (length(gpusat4_times) > 0)    as.numeric(1:length(gpusat4_times))else  c()

gpusat_vbest_times <-
  as.numeric((
    pmin(
      gpusat1_times_,
      gpusat2_times_,
      gpusat3_times_,
      gpusat4_times_
    )
  ))
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

gpusat1_times <- gpusat1_times[order(gpusat_vbest_times)]
gpusat2_times <- gpusat2_times[order(gpusat_vbest_times)]
gpusat3_times <- gpusat3_times[order(gpusat_vbest_times)]
gpusat4_times <- gpusat4_times[order(gpusat_vbest_times)]
gpusat_vbest_times <-  gpusat_vbest_times[order(gpusat_vbest_times)]

plot(
  range(0:length(gpusat_vbest_times) + 1),
  range(
    0:max(gpusat1_times, gpusat2_times, gpusat3_times, gpusat4_times)
  ),
  type = "n",
  xlab = "Instances",
  ylab = "Time",
  lab = c(20, 10, 7)
)
lines(
  gpusat1_numbers,
  gpusat1_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "green",
  pch = "."
)
lines(
  gpusat2_numbers,
  gpusat2_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "red",
  pch = "."
)
lines(
  gpusat3_numbers,
  gpusat3_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "cyan",
  pch = "."
)
lines(
  gpusat4_numbers,
  gpusat4_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "violet",
  pch = "."
)
lines(
  gpusat_vbest_numbers,
  gpusat_vbest_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "blue",
  pch = "."
)
title(PlotTitle)
legend(
  0,-0.1,
  xpd = TRUE,
  c(name1, name2, name3, name4, "best"),
  cex = 0.8,
  col = c("green", "red", "cyan", "violet", "blue"),
  lty = "solid",
  title = "solver"
)

```

## gpusat vs. approxmc 

```{r gpusat vs. approxmc, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
generateInstanceKaktusPlot(
  "gpusat primal vs. approxmc",
  Results$setting == "primal_double_w-14_m-24",
  Results$solver == "approxmc",
  "gpusat_primal-vs-approxmc.png",
  "gpusat primal",
  "approxmc"
)
generateInstanceKaktusPlot(
  "gpusat incidence vs. approxmc",
  Results$setting == "incidence_double_w-14_m-24",
  Results$solver == "approxmc",
  "gpusat_incidence-vs-approxmc.png",
  "gpusat incidence",
  "approxmc"
)

```

## gpusat (vbest) vs. approxmc

```{r gpusat (vbest) vs. approxmc, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_1 <-  Results$time[Results$setting == "primal_double_w-14_m-24"]
gpusat1_times_2 <-  Results$time[Results$setting == "incidence_double_w-14_m-24"]
gpusat2_times_ <- Results$time[Results$solver == "approxmc"]

gpusat1_times <-  as.numeric(sort(pmin(gpusat1_times_1, gpusat1_times_2)))
gpusat1_times <- gpusat1_times[gpusat1_times < 900]
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <-  as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <-  as.numeric(sort(pmin(    gpusat1_times_1, gpusat1_times_2, gpusat2_times_  )))
gpusat_vbest_times <- gpusat_vbest_times[gpusat_vbest_times < 900]
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

# set up the plot
plot(
  range(0:length(gpusat_vbest_times) + 1),
  range(0:max(gpusat1_times, gpusat2_times)),
  type = "n",
  xlab = "Instances",
  ylab = "Time",
  lab = c(20, 10, 7)
)

# add lines
lines(
  gpusat1_numbers,
  gpusat1_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "green",
  pch = "."
)
lines(
  gpusat2_numbers,
  gpusat2_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "red",
  pch = "."
)
lines(
  gpusat_vbest_numbers,
  gpusat_vbest_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "blue",
  pch = "."
)

# add a title and subtitle
title("gpusat vs. approxmc")

# add a legend
legend(
  0,
  max(gpusat1_times, gpusat2_times),
  xpd = TRUE,
  c("gpusat", "approxmc", "best"),
  cex = 0.8,
  col = c("green", "red", "blue"),
  lty = "solid",
  title = "solver"
)

# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_1 <-  Results$time[Results$setting == "primal_double_w-14_m-24"]
gpusat1_times_2 <-  Results$time[Results$setting == "incidence_double_w-14_m-24"]
gpusat2_times_ <- Results$time[Results$solver == "approxmc"]

gpusat1_times <- as.numeric(pmin(gpusat1_times_1, gpusat1_times_2))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <- as.numeric((gpusat2_times_))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))

gpusat_vbest_times <-  as.numeric((pmin(    gpusat1_times_1, gpusat1_times_2, gpusat2_times_  )))
gpusat_vbest_numbers <- as.numeric(1:length(gpusat_vbest_times))

gpusat1_times <- gpusat1_times[order(gpusat_vbest_times)]
gpusat2_times <- gpusat2_times[order(gpusat_vbest_times)]
gpusat_vbest_times <- gpusat_vbest_times[order(gpusat_vbest_times)]

# set up the plot
plot(
  range(0:length(gpusat_vbest_times) + 1),
  range(0:max(gpusat1_times, gpusat2_times)),
  type = "n",
  xlab = "Instances",
  ylab = "Time",
  lab = c(20, 10, 7)
)

# add lines
lines(
  gpusat1_numbers,
  gpusat1_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "green",
  pch = "."
)
lines(
  gpusat2_numbers,
  gpusat2_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "red",
  pch = "."
)
lines(
  gpusat_vbest_numbers,
  gpusat_vbest_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "blue",
  pch = "."
)

# add a title and subtitle
title("gpusat vs. approxmc")

# add a legend
legend(
  0,
  max(gpusat1_times, gpusat2_times),
  xpd = TRUE,
  c("gpusat", "approxmc", "best"),
  cex = 0.8,
  col = c("green", "red", "blue"),
  lty = "solid",
  title = "solver"
)

```

## gpusat vs. sharpSAT 

```{r gpusat vs. sharpSAT, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
generateInstanceKaktusPlot(
  "gpusat primal vs. sharpSAT",
  Results$setting == "primal_double_w-14_m-24",
  Results$solver == "sharpSAT",
  "gpusat_primal-vs-sharpSAT.png",
  "gpusat primal",
  "sharpSAT"
)
generateInstanceKaktusPlot(
  "gpusat incidence vs. sharpSAT",
  Results$setting == "incidence_double_w-14_m-24",
  Results$solver == "sharpSAT",
  "gpusat_incidence-vs-sharpSAT.png",
  "gpusat incidence",
  "sharpSAT"
)

```

## gpusat vs. cachet

```{r gpusat vs. cachet, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
generateInstanceKaktusPlot(
  "gpusat primal vs. cachet",
  Results$setting == "primal_double_w-14_m-24",
  Results$solver == "cachet",
  "gpusat_primal-vs-cachet.png",
  "gpusat primal",
  "cachet"
)
generateInstanceKaktusPlot(
  "gpusat incidence vs. cachet",
  Results$setting == "incidence_double_w-14_m-24",
  Results$solver == "cachet",
  "gpusat_incidence-vs-cachet.png",
  "gpusat incidence",
  "cachet"
)

```

## gpusat vs. dsharp

```{r gpusat vs. dsharp, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
generateInstanceKaktusPlot(
  "gpusat primal vs. dsharp",
  Results$setting == "primal_double_w-14_m-24",
  Results$solver == "dsharp",
  "gpusat_primal-vs-dsharp.png",
  "gpusat primal",
  "dsharp"
)
generateInstanceKaktusPlot(
  "gpusat incidence vs. dsharp",
  Results$setting == "incidence_double_w-14_m-24",
  Results$solver == "dsharp",
  "gpusat_incidence-vs-dsharp.png",
  "gpusat incidence",
  "dsharp"
)

```

## gpusat vs. sharpSAT vs. cachet vs. dsharp vs. approxmc

```{r gpusat vs. sharpSAT vs. cachet vs. dsharp vs. approxmc, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_ <-  Results$time[Results$setting == "primal_double_w-14_m-24"]
gpusat2_times_ <-  Results$time[Results$setting == "incidence_double_w-14_m-24"]
gpusat3_times_ <- Results$time[Results$solver == "sharpSAT"]
gpusat4_times_ <- Results$time[Results$solver == "cachet"]
gpusat5_times_ <- Results$time[Results$solver == "dsharp"]
gpusat6_times_ <- Results$time[Results$solver == "approxmc"]
gpusat7_times_ <- Results$time[Results$solver == "clasp"]
gpusat8_times_ <- Results$time[Results$solver == "lingeling"]
gpusat9_times_ <- Results$time[Results$solver == "minisat"]
gpusat10_times_ <- Results$time[Results$solver == "picosat"]
gpusat11_times_ <- Results$time[Results$solver == "cryptominisat"]

gpusat1_times <-  as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <-  as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))
gpusat3_times <-  as.numeric(sort(gpusat3_times_[gpusat3_times_ < 900]))
gpusat3_numbers <- as.numeric(1:length(gpusat3_times))
gpusat4_times <-  as.numeric(sort(gpusat4_times_[gpusat4_times_ < 900]))
gpusat4_numbers <- as.numeric(1:length(gpusat4_times))
gpusat5_times <-  as.numeric(sort(gpusat5_times_[gpusat5_times_ < 900]))
gpusat5_numbers <- as.numeric(1:length(gpusat5_times))
gpusat6_times <-  as.numeric(sort(gpusat6_times_[gpusat6_times_ < 900]))
gpusat6_numbers <- as.numeric(1:length(gpusat6_times))
gpusat7_times <-  as.numeric(sort(gpusat7_times_[gpusat7_times_ < 900]))
gpusat7_numbers <- as.numeric(1:length(gpusat7_times))
gpusat8_times <-  as.numeric(sort(gpusat8_times_[gpusat8_times_ < 900]))
gpusat8_numbers <- as.numeric(1:length(gpusat8_times))
gpusat9_times <-  as.numeric(sort(gpusat9_times_[gpusat9_times_ < 900]))
gpusat9_numbers <- as.numeric(1:length(gpusat9_times))
gpusat10_times <-  as.numeric(sort(gpusat10_times_[gpusat10_times_ < 900]))
gpusat10_numbers <- as.numeric(1:length(gpusat10_times))
gpusat11_times <-  as.numeric(sort(gpusat11_times_[gpusat11_times_ < 900]))
gpusat11_numbers <- as.numeric(1:length(gpusat11_times))

# set up the plot
plot(
  range(0:length(gpusat_vbest_times) + 1),
  range(
    0:max(
      gpusat1_times,
      gpusat2_times,
      gpusat3_times,
      gpusat4_times,
      gpusat5_times,
      gpusat6_times,
      gpusat7_times,
      gpusat8_times,
      gpusat9_times,
      gpusat10_times,
      gpusat11_times
    )
  ),
  type = "n",
  xlab = "Instances",
  ylab = "Time",
  lab = c(20, 10, 7)
)

# add lines
lines(
  gpusat1_numbers,
  gpusat1_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "red",
  pch = "."
)
lines(
  gpusat2_numbers,
  gpusat2_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "green",
  pch = "."
)
lines(
  gpusat3_numbers,
  gpusat3_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "yellow",
  pch = "."
)
lines(
  gpusat4_numbers,
  gpusat4_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "violet",
  pch = "."
)
lines(
  gpusat5_numbers,
  gpusat5_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "brown",
  pch = "."
)
lines(
  gpusat6_numbers,
  gpusat6_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "orange",
  pch = "."
)
lines(
  gpusat7_numbers,
  gpusat7_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "gold",
  pch = "."
)
lines(
  gpusat8_numbers,
  gpusat8_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "coral",
  pch = "."
)
lines(
  gpusat9_numbers,
  gpusat9_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "cyan",
  pch = "."
)
lines(
  gpusat10_numbers,
  gpusat10_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "darkgreen",
  pch = "."
)
lines(
  gpusat11_numbers,
  gpusat11_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "darkmagenta",
  pch = "."
)

# add a title and subtitle
title("primal_double_w-14_m-24 vs. sharpSAT vs. cachet")

# add a legend
legend(
  0,
  max(
    gpusat1_times,
    gpusat2_times,
    gpusat3_times,
    gpusat4_times,
    gpusat5_times,
    gpusat6_times,
    gpusat7_times,
    gpusat8_times,
    gpusat9_times,
    gpusat10_times,
    gpusat11_times
  ),
  xpd = TRUE,
  c(
    "primal_double_w-14_m-24",
    "incidence_double_w-14_m-24",
    "sharpSAT",
    "cachet",
    "dsharp",
    "approxmc",
    "clasp",
    "lingeling",
    "minisat",
    "picosat",
    "cryptominisat"
  ),
  cex = 0.8,
  col = c(
    "red",
    "green",
    "yellow",
    "violet",
    "brown",
    "orange",
    "gold",
    "coral",
    "cyan",
    "darkgreen",
    "darkmagenta"
  ),
  lty = "solid",
  title = "solver"
)

```

## gpusat vs. sat

```{r gpusat vs. sat, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_ <-  Results$time[Results$setting == "primal_double_w-14_m-24" &                 Results$instance %in% Instances_Primal_Width_0_20]
gpusat2_times_ <-  Results$time[Results$setting == "incidence_double_w-14_m-24" &                 Results$instance %in% Instances_Primal_Width_0_20]
gpusat7_times_ <- Results$time[Results$solver == "clasp" &                                 Results$instance %in% Instances_Primal_Width_0_20]
gpusat8_times_ <- Results$time[Results$solver == "lingeling" &                                 Results$instance %in% Instances_Primal_Width_0_20]
gpusat9_times_ <- Results$time[Results$solver == "minisat" &                                 Results$instance %in% Instances_Primal_Width_0_20]
gpusat10_times_ <- Results$time[Results$solver == "picosat" &                                  Results$instance %in% Instances_Primal_Width_0_20]
gpusat11_times_ <- Results$time[Results$solver == "cryptominisat" &                                  Results$instance %in% Instances_Primal_Width_0_20]
gpusat12_times_ <- Results$time[Results$setting == "dynasp_primal" &                                  Results$instance %in% Instances_Primal_Width_0_20]
gpusat13_times_ <-  Results$time[Results$setting == "dynasp_incidence" &                 Results$instance %in% Instances_Primal_Width_0_20]

gpusat1_times <-  as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <-  as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))
gpusat7_times <-  as.numeric(sort(gpusat7_times_[gpusat7_times_ < 900]))
gpusat7_numbers <- as.numeric(1:length(gpusat7_times))
gpusat8_times <-  as.numeric(sort(gpusat8_times_[gpusat8_times_ < 900]))
gpusat8_numbers <- as.numeric(1:length(gpusat8_times))
gpusat9_times <-  as.numeric(sort(gpusat9_times_[gpusat9_times_ < 900]))
gpusat9_numbers <- as.numeric(1:length(gpusat9_times))
gpusat10_times <-  as.numeric(sort(gpusat10_times_[gpusat10_times_ < 900]))
gpusat10_numbers <- as.numeric(1:length(gpusat10_times))
gpusat11_times <-  as.numeric(sort(gpusat11_times_[gpusat11_times_ < 900]))
gpusat11_numbers <- as.numeric(1:length(gpusat11_times))
gpusat12_times <-  as.numeric(sort(gpusat12_times_[gpusat12_times_ < 900]))
gpusat12_numbers <- as.numeric(1:length(gpusat12_times))
gpusat13_times <-  as.numeric(sort(gpusat13_times_[gpusat13_times_ < 900]))
gpusat13_numbers <- as.numeric(1:length(gpusat13_times))

# set up the plot
plot(
  range(
    0:max(
      length(gpusat1_numbers),
      length(gpusat2_numbers),
      length(gpusat7_numbers),
      length(gpusat8_numbers),
      length(gpusat9_numbers),
      length(gpusat10_numbers),
      length(gpusat11_numbers),
      length(gpusat12_numbers),
      length(gpusat13_numbers)
    )
  ),
  range(
    0:max(
      gpusat1_times,
      gpusat2_times,
      gpusat7_times,
      gpusat8_times,
      gpusat9_times,
      gpusat10_times,
      gpusat11_times,
      gpusat12_times,
      gpusat13_times
    )
  ),
  type = "n",
  xlab = "Instances",
  ylab = "Time",
  lab = c(20, 10, 7)
)

# add lines
lines(
  gpusat1_numbers,
  gpusat1_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "red",
  pch = "."
)
lines(
  gpusat2_numbers,
  gpusat2_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "green",
  pch = "."
)
lines(
  gpusat7_numbers,
  gpusat7_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "gold",
  pch = "."
)
lines(
  gpusat8_numbers,
  gpusat8_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "coral",
  pch = "."
)
lines(
  gpusat9_numbers,
  gpusat9_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "cyan",
  pch = "."
)
lines(
  gpusat10_numbers,
  gpusat10_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "darkgreen",
  pch = "."
)
lines(
  gpusat11_numbers,
  gpusat11_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "darkmagenta",
  pch = "."
)
lines(
  gpusat12_numbers,
  gpusat12_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "black",
  pch = "."
)
lines(
  gpusat13_numbers,
  gpusat13_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "grey",
  pch = "."
)

# add a title and subtitle
title("gpusat vs. sat")

# add a legend
legend(
  0,
  max(
    gpusat1_times,
    gpusat2_times,
    gpusat7_times,
    gpusat8_times,
    gpusat9_times,
    gpusat10_times,
    gpusat11_times,
    gpusat12_times,
    gpusat13_times
  ),
  xpd = TRUE,
  c(
    "primal_double_w-14_m-24",
    "incidence_double_w-14_m-24",
    "clasp",
    "lingeling",
    "minisat",
    "picosat",
    "cryptominisat",
    "dynasp_primal",
    "dynasp_incidence"
  ),
  cex = 0.8,
  col = c(
    "red",
    "green",
    "gold",
    "coral",
    "cyan",
    "darkgreen",
    "darkmagenta",
    "black",
    "grey"
  ),
  lty = "solid",
  title = "solver"
)

```

## gpusat vs. sat sat

```{r gpusat vs. sat sat, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_ <-  Results$time[Results$setting == "primal_double_w-14_m-24" &                 Results$instance %in% Instances_Primal_Width_0_20 &                 Results$instance %in% Instances_SAT]
gpusat2_times_ <-  Results$time[Results$setting == "incidence_double_w-14_m-24" &                 Results$instance %in% Instances_Primal_Width_0_20 &                 Results$instance %in% Instances_SAT]
gpusat7_times_ <- Results$time[Results$solver == "clasp" &                                 Results$instance %in% Instances_Primal_Width_0_20 &                                 Results$instance %in% Instances_SAT]
gpusat8_times_ <- Results$time[Results$solver == "lingeling" &                                 Results$instance %in% Instances_Primal_Width_0_20 &                                 Results$instance %in% Instances_SAT]
gpusat9_times_ <- Results$time[Results$solver == "minisat" &                                 Results$instance %in% Instances_Primal_Width_0_20 &                                 Results$instance %in% Instances_SAT]
gpusat10_times_ <- Results$time[Results$solver == "picosat" &                                  Results$instance %in% Instances_Primal_Width_0_20 &                                  Results$instance %in% Instances_SAT]
gpusat11_times_ <- Results$time[Results$solver == "cryptominisat" &                                  Results$instance %in% Instances_Primal_Width_0_20 &                                  Results$instance %in% Instances_SAT]
gpusat12_times_ <- Results$time[Results$setting == "dynasp_primal" &                                  Results$instance %in% Instances_Primal_Width_0_20 &                                  Results$instance %in% Instances_SAT]
gpusat13_times_ <-  Results$time[Results$setting == "dynasp_incidence" &                 Results$instance %in% Instances_Primal_Width_0_20 &                 Results$instance %in% Instances_SAT]

gpusat1_times <-  as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <-  as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))
gpusat7_times <-  as.numeric(sort(gpusat7_times_[gpusat7_times_ < 900]))
gpusat7_numbers <- as.numeric(1:length(gpusat7_times))
gpusat8_times <-  as.numeric(sort(gpusat8_times_[gpusat8_times_ < 900]))
gpusat8_numbers <- as.numeric(1:length(gpusat8_times))
gpusat9_times <-  as.numeric(sort(gpusat9_times_[gpusat9_times_ < 900]))
gpusat9_numbers <- as.numeric(1:length(gpusat9_times))
gpusat10_times <-  as.numeric(sort(gpusat10_times_[gpusat10_times_ < 900]))
gpusat10_numbers <- as.numeric(1:length(gpusat10_times))
gpusat11_times <-  as.numeric(sort(gpusat11_times_[gpusat11_times_ < 900]))
gpusat11_numbers <- as.numeric(1:length(gpusat11_times))
gpusat12_times <-  as.numeric(sort(gpusat12_times_[gpusat12_times_ < 900]))
gpusat12_numbers <- as.numeric(1:length(gpusat12_times))
gpusat13_times <-  as.numeric(sort(gpusat13_times_[gpusat13_times_ < 900]))
gpusat13_numbers <- as.numeric(1:length(gpusat13_times))

# set up the plot
plot(
  range(
    0:max(
      length(gpusat1_numbers),
      length(gpusat2_numbers),
      length(gpusat7_numbers),
      length(gpusat8_numbers),
      length(gpusat9_numbers),
      length(gpusat10_numbers),
      length(gpusat11_numbers),
      length(gpusat12_numbers),
      length(gpusat13_numbers)
    )
  ),
  range(
    0:max(
      gpusat1_times,
      gpusat2_times,
      gpusat7_times,
      gpusat8_times,
      gpusat9_times,
      gpusat10_times,
      gpusat11_times,
      gpusat12_times,
      gpusat13_times
    )
  ),
  type = "n",
  xlab = "Instances",
  ylab = "Time",
  lab = c(20, 10, 7)
)

# add lines
lines(
  gpusat1_numbers,
  gpusat1_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "red",
  pch = "."
)
lines(
  gpusat2_numbers,
  gpusat2_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "green",
  pch = "."
)
lines(
  gpusat7_numbers,
  gpusat7_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "gold",
  pch = "."
)
lines(
  gpusat8_numbers,
  gpusat8_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "coral",
  pch = "."
)
lines(
  gpusat9_numbers,
  gpusat9_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "cyan",
  pch = "."
)
lines(
  gpusat10_numbers,
  gpusat10_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "darkgreen",
  pch = "."
)
lines(
  gpusat11_numbers,
  gpusat11_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "darkmagenta",
  pch = "."
)
lines(
  gpusat12_numbers,
  gpusat12_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "black",
  pch = "."
)
lines(
  gpusat13_numbers,
  gpusat13_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "grey",
  pch = "."
)

# add a title and subtitle
title("gpusat vs. sat")

# add a legend
legend(
  0,
  max(
    gpusat1_times,
    gpusat2_times,
    gpusat7_times,
    gpusat8_times,
    gpusat9_times,
    gpusat10_times,
    gpusat11_times,
    gpusat12_times,
    gpusat13_times
  ),
  xpd = TRUE,
  c(
    "primal_double_w-14_m-24",
    "incidence_double_w-14_m-24",
    "clasp",
    "lingeling",
    "minisat",
    "picosat",
    "cryptominisat",
    "dynasp_primal",
    "dynasp_incidence"
  ),
  cex = 0.8,
  col = c(
    "red",
    "green",
    "gold",
    "coral",
    "cyan",
    "darkgreen",
    "darkmagenta",
    "black",
    "grey"
  ),
  lty = "solid",
  title = "solver"
)

```

## gpusat vs. sat unsat

```{r gpusat vs. sat unsat, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Create Line Chart
# convert factor to numeric for convenience
gpusat1_times_ <-  Results$time[Results$setting == "primal_double_w-14_m-24" &                 Results$instance %in% Instances_Primal_Width_0_20 &                 Results$instance %in% Instances_UNSAT]
gpusat2_times_ <-  Results$time[Results$setting == "incidence_double_w-14_m-24" &                 Results$instance %in% Instances_Primal_Width_0_20 &                 Results$instance %in% Instances_UNSAT]
gpusat7_times_ <- Results$time[Results$solver == "clasp" &                                 Results$instance %in% Instances_Primal_Width_0_20 &                                 Results$instance %in% Instances_UNSAT]
gpusat8_times_ <- Results$time[Results$solver == "lingeling" &                                 Results$instance %in% Instances_Primal_Width_0_20 &                                 Results$instance %in% Instances_UNSAT]
gpusat9_times_ <- Results$time[Results$solver == "minisat" &                                 Results$instance %in% Instances_Primal_Width_0_20 &                                 Results$instance %in% Instances_UNSAT]
gpusat10_times_ <- Results$time[Results$solver == "picosat" &                                  Results$instance %in% Instances_Primal_Width_0_20 &                                  Results$instance %in% Instances_UNSAT]
gpusat11_times_ <- Results$time[Results$solver == "cryptominisat" &                                  Results$instance %in% Instances_Primal_Width_0_20 &                                  Results$instance %in% Instances_UNSAT]
gpusat12_times_ <- Results$time[Results$setting == "dynasp_primal" &                                  Results$instance %in% Instances_Primal_Width_0_20 &                                  Results$instance %in% Instances_UNSAT]
gpusat13_times_ <-  Results$time[Results$setting == "dynasp_incidence" &                 Results$instance %in% Instances_Primal_Width_0_20 &                 Results$instance %in% Instances_UNSAT]

gpusat1_times <-  as.numeric(sort(gpusat1_times_[gpusat1_times_ < 900]))
gpusat1_numbers <- as.numeric(1:length(gpusat1_times))
gpusat2_times <-  as.numeric(sort(gpusat2_times_[gpusat2_times_ < 900]))
gpusat2_numbers <- as.numeric(1:length(gpusat2_times))
gpusat7_times <-  as.numeric(sort(gpusat7_times_[gpusat7_times_ < 900]))
gpusat7_numbers <- as.numeric(1:length(gpusat7_times))
gpusat8_times <-  as.numeric(sort(gpusat8_times_[gpusat8_times_ < 900]))
gpusat8_numbers <- as.numeric(1:length(gpusat8_times))
gpusat9_times <-  as.numeric(sort(gpusat9_times_[gpusat9_times_ < 900]))
gpusat9_numbers <- as.numeric(1:length(gpusat9_times))
gpusat10_times <-  as.numeric(sort(gpusat10_times_[gpusat10_times_ < 900]))
gpusat10_numbers <- as.numeric(1:length(gpusat10_times))
gpusat11_times <-  as.numeric(sort(gpusat11_times_[gpusat11_times_ < 900]))
gpusat11_numbers <- as.numeric(1:length(gpusat11_times))
gpusat12_times <-  as.numeric(sort(gpusat12_times_[gpusat12_times_ < 900]))
gpusat12_numbers <- as.numeric(1:length(gpusat12_times))
gpusat13_times <-  as.numeric(sort(gpusat13_times_[gpusat13_times_ < 900]))
gpusat13_numbers <- as.numeric(1:length(gpusat13_times))

# set up the plot
plot(
  range(
    0:max(
      length(gpusat1_numbers),
      length(gpusat2_numbers),
      length(gpusat7_numbers),
      length(gpusat8_numbers),
      length(gpusat9_numbers),
      length(gpusat10_numbers),
      length(gpusat11_numbers),
      length(gpusat12_numbers),
      length(gpusat13_numbers)
    )
  ),
  range(
    0:max(
      gpusat1_times,
      gpusat2_times,
      gpusat7_times,
      gpusat8_times,
      gpusat9_times,
      gpusat10_times,
      gpusat11_times,
      gpusat12_times,
      gpusat13_times
    )
  ),
  type = "n",
  xlab = "Instances",
  ylab = "Time",
  lab = c(20, 10, 7)
)

# add lines
lines(
  gpusat1_numbers,
  gpusat1_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "red",
  pch = "."
)
lines(
  gpusat2_numbers,
  gpusat2_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "green",
  pch = "."
)
lines(
  gpusat7_numbers,
  gpusat7_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "gold",
  pch = "."
)
lines(
  gpusat8_numbers,
  gpusat8_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "coral",
  pch = "."
)
lines(
  gpusat9_numbers,
  gpusat9_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "cyan",
  pch = "."
)
lines(
  gpusat10_numbers,
  gpusat10_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "darkgreen",
  pch = "."
)
lines(
  gpusat11_numbers,
  gpusat11_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "darkmagenta",
  pch = "."
)
lines(
  gpusat12_numbers,
  gpusat12_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "darkred",
  pch = "."
)
lines(
  gpusat13_numbers,
  gpusat13_times,
  type = "l",
  lwd = 0.5,
  lty = "solid",
  col = "darkgreen",
  pch = "."
)

# add a title and subtitle
title("gpusat vs. sat")

# add a legend
legend(
  0,
  max(
    gpusat1_times,
    gpusat2_times,
    gpusat7_times,
    gpusat8_times,
    gpusat9_times,
    gpusat10_times,
    gpusat11_times,
    gpusat12_times,
    gpusat13_times
  ),
  xpd = TRUE,
  c(
    "primal_double_w-14_m-24",
    "incidence_double_w-14_m-24",
    "clasp",
    "lingeling",
    "minisat",
    "picosat",
    "cryptominisat",
    "dynasp_primal",
    "dynasp_incidence"
  ),
  cex = 0.8,
  col = c(
    "red",
    "green",
    "gold",
    "coral",
    "cyan",
    "darkgreen",
    "darkmagenta",
    "darkred",
    "darkgreen"
  ),
  lty = "solid",
  title = "solver"
)

```

## SAT gpusat vs. dynasp

```{r SAT gpusat vs. dynasp kaktus, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
generateInstanceKaktusPlot(
  "gpusat vs. dynasp primal SAT",
  Results$setting == "primal_double_w-14_m-24" &
    Results$instance %in% Instances_SAT,
  Results$setting == "dynasp_primal" &
    Results$instance %in% Instances_SAT,
  "gpusat_primal-vs-dynasp-SAT.png",
  "gpusat primal",
  "dynasp primal"
)

generateInstanceKaktusPlot(
  "gpusat vs. dynasp incidence SAT",
  Results$setting == "incidence_double_w-14_m-24" &
    Results$instance %in% Instances_SAT,
  Results$setting == "dynasp_incidence" &
    Results$instance %in% Instances_SAT,
  "gpusat_incidence-vs-dynasp-SAT.png",
  "gpusat incidence",
  "dynasp incidence"
)

```

## UNSAT gpusat vs. dynasp

```{r UNSAT gpusat vs. dynasp kaktus, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
generateInstanceKaktusPlot(
  "gpusat vs. dynasp primal UNSAT",
  Results$setting == "primal_double_w-14_m-24" &
    Results$instance %in% Instances_UNSAT,
  Results$setting == "dynasp_primal" &
    Results$instance %in% Instances_UNSAT,
  "gpusat_primal-vs-dynasp-UNSAT.png",
  "gpusat primal",
  "dynasp primal"
)

generateInstanceKaktusPlot(
  "gpusat vs. dynasp incidence UNSAT",
  Results$setting == "incidence_double_w-14_m-24" &
    Results$instance %in% Instances_UNSAT,
  Results$setting == "dynasp_incidence" &
    Results$instance %in% Instances_UNSAT,
  "gpusat_incidence-vs-dynasp-UNSAT.png",
  "gpusat incidence",
  "dynasp incidence"
)

```

## gpusat vs. dynasp vs dynqbf vs. sharpSAT: Width 1-15

```{r gpusat vs. dynasp vs dynqbf vs. sharpSAT: Width 1-15, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT primal: Width 1-15",
  Results$setting == "primal_double_w-14_m-24" &
    Results$instance %in% Instances_Primal_Width_1_15,
  Results$setting == "dynasp_primal" &
    Results$instance %in% Instances_Primal_Width_1_15,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Primal_Width_1_15,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Primal_Width_1_15,
  "gpusat_primal-vs-dynasp-Width_1-15.png",
  "gpusat primal",
  "dynasp primal",
  "dynqbf",
  "sharpSAT"
)

generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT incidence: Width 1-15",
  Results$setting == "incidence_double_w-14_m-24" &
    Results$instance %in% Instances_Incidence_Width_1_15,
  Results$setting == "dynasp_incidence" &
    Results$instance %in% Instances_Incidence_Width_1_15,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Incidence_Width_1_15,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Incidence_Width_1_15,
  "gpusat_incidence-vs-dynasp-Width_1-15.png",
  "gpusat incidence",
  "dynasp incidence",
  "dynqbf",
  "sharpSAT"
)

```

## gpusat vs. dynasp vs dynqbf vs. sharpSAT: Width 16-20

```{r gpusat vs. dynasp vs dynqbf vs. sharpSAT: Width 16-20, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT primal: Width 16-20",
  Results$setting == "primal_double_w-14_m-24" &
    Results$instance %in% Instances_Primal_Width_16_20,
  Results$setting == "dynasp_primal" &
    Results$instance %in% Instances_Primal_Width_16_20,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Primal_Width_16_20,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Primal_Width_16_20,
  "gpusat_primal-vs-dynasp-Width_16-20.png",
  "gpusat primal",
  "dynasp primal",
  "dynqbf",
  "sharpSAT"
)

generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT incidence: Width 16-20",
  Results$setting == "incidence_double_w-14_m-24" &
    Results$instance %in% Instances_Incidence_Width_16_20,
  Results$setting == "dynasp_incidence" &
    Results$instance %in% Instances_Incidence_Width_16_20,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Incidence_Width_16_20,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Incidence_Width_16_20,
  "gpusat_incidence-vs-dynasp-Width_16-20.png",
  "gpusat incidence",
  "dynasp incidence",
  "dynqbf",
  "sharpSAT"
)

```

## gpusat vs. dynasp vs dynqbf vs. sharpSAT: Width 21-25

```{r gpusat vs. dynasp vs dynqbf vs. sharpSAT: Width 21-25, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT primal: Width 21-25",
  Results$setting == "primal_double_w-14_m-24" &
    Results$instance %in% Instances_Primal_Width_21_25,
  Results$setting == "dynasp_primal" &
    Results$instance %in% Instances_Primal_Width_21_25,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Primal_Width_21_25,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Primal_Width_21_25,
  "gpusat_primal-vs-dynasp-Width_21-25.png",
  "gpusat primal",
  "dynasp primal",
  "dynqbf",
  "sharpSAT"
)

generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT incidence: Width 21-25",
  Results$setting == "incidence_double_w-14_m-24" &
    Results$instance %in% Instances_Incidence_Width_21_25,
  Results$setting == "dynasp_incidence" &
    Results$instance %in% Instances_Incidence_Width_21_25,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Incidence_Width_21_25,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Incidence_Width_21_25,
  "gpusat_incidence-vs-dynasp-Width_21-25.png",
  "gpusat incidence",
  "dynasp incidence",
  "dynqbf",
  "sharpSAT"
)

```

## gpusat vs. dynasp vs dynqbf vs. sharpSAT: Width 26-30

```{r gpusat vs. dynasp vs dynqbf vs. sharpSAT: Width 26-30, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT primal: Width 26-30",
  Results$setting == "primal_double_w-14_m-24" &
    Results$instance %in% Instances_Primal_Width_26_30,
  Results$setting == "dynasp_primal" &
    Results$instance %in% Instances_Primal_Width_26_30,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Primal_Width_26_30,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Primal_Width_26_30,
  "gpusat_primal-vs-dynasp-Width_26-30.png",
  "gpusat primal",
  "dynasp primal",
  "dynqbf",
  "sharpSAT"
)

generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT incidence: Width 26-30",
  Results$setting == "incidence_double_w-14_m-24" &
    Results$instance %in% Instances_Incidence_Width_26_30,
  Results$setting == "dynasp_incidence" &
    Results$instance %in% Instances_Incidence_Width_26_30,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Incidence_Width_26_30,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Incidence_Width_26_30,
  "gpusat_incidence-vs-dynasp-Width_26-30.png",
  "gpusat incidence",
  "dynasp incidence",
  "dynqbf",
  "sharpSAT"
)

```

## gpusat vs. dynasp vs dynqbf vs. sharpSAT: Width 31-40

```{r gpusat vs. dynasp vs dynqbf vs. sharpSAT: Width 31-40, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT primal: Width 31-40",
  Results$setting == "primal_double_w-14_m-24" &
    Results$instance %in% Instances_Primal_Width_31_40,
  Results$setting == "dynasp_primal" &
    Results$instance %in% Instances_Primal_Width_31_40,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Primal_Width_31_40,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Primal_Width_31_40,
  "gpusat_primal-vs-dynasp-Width_31-40.png",
  "gpusat primal",
  "dynasp primal",
  "dynqbf",
  "sharpSAT"
)

generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT incidence: Width 31-40",
  Results$setting == "incidence_double_w-14_m-24" &
    Results$instance %in% Instances_Incidence_Width_31_40,
  Results$setting == "dynasp_incidence" &
    Results$instance %in% Instances_Incidence_Width_31_40,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Incidence_Width_31_40,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Incidence_Width_31_40,
  "gpusat_incidence-vs-dynasp-Width_31-40.png",
  "gpusat incidence",
  "dynasp incidence",
  "dynqbf",
  "sharpSAT"
)

```

## gpusat vs. dynasp vs dynqbf vs. sharpSAT SAT: Width 1-15

```{r gpusat vs. dynasp vs dynqbf vs. sharpSAT SAT: Width 1-15, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT primal: Width 1-15",
  Results$setting == "primal_double_w-14_m-24" &
    Results$instance %in% Instances_Primal_Width_1_15 &
    Results$instance %in% Instances_SAT,
  Results$setting == "dynasp_primal" &
    Results$instance %in% Instances_Primal_Width_1_15 &
    Results$instance %in% Instances_SAT,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Primal_Width_1_15 &
    Results$instance %in% Instances_SAT,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Primal_Width_1_15 &
    Results$instance %in% Instances_SAT,
  "gpusat_primal-vs-dynasp-Width_1-15.png",
  "gpusat primal",
  "dynasp primal",
  "dynqbf",
  "sharpSAT"
)

generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT incidence: Width 1-15",
  Results$setting == "incidence_double_w-14_m-24" &
    Results$instance %in% Instances_Incidence_Width_1_15 &
    Results$instance %in% Instances_SAT,
  Results$setting == "dynasp_incidence" &
    Results$instance %in% Instances_Incidence_Width_1_15 &
    Results$instance %in% Instances_SAT,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Incidence_Width_1_15 &
    Results$instance %in% Instances_SAT,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Incidence_Width_1_15 &
    Results$instance %in% Instances_SAT,
  "gpusat_incidence-vs-dynasp-Width_1-15.png",
  "gpusat incidence",
  "dynasp incidence",
  "dynqbf",
  "sharpSAT"
)

```

## gpusat vs. dynasp vs dynqbf vs. sharpSAT SAT: Width 16-20

```{r gpusat vs. dynasp vs dynqbf vs. sharpSAT SAT: Width 16-20, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT primal: Width 16-20",
  Results$setting == "primal_double_w-14_m-24" &
    Results$instance %in% Instances_Primal_Width_16_20 &
    Results$instance %in% Instances_SAT,
  Results$setting == "dynasp_primal" &
    Results$instance %in% Instances_Primal_Width_16_20 &
    Results$instance %in% Instances_SAT,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Primal_Width_16_20 &
    Results$instance %in% Instances_SAT,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Primal_Width_16_20 &
    Results$instance %in% Instances_SAT,
  "gpusat_primal-vs-dynasp-Width_16-20.png",
  "gpusat primal",
  "dynasp primal",
  "dynqbf",
  "sharpSAT"
)

generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT incidence: Width 16-20",
  Results$setting == "incidence_double_w-14_m-24" &
    Results$instance %in% Instances_Incidence_Width_16_20 &
    Results$instance %in% Instances_SAT,
  Results$setting == "dynasp_incidence" &
    Results$instance %in% Instances_Incidence_Width_16_20 &
    Results$instance %in% Instances_SAT,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Incidence_Width_16_20 &
    Results$instance %in% Instances_SAT,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Incidence_Width_16_20 &
    Results$instance %in% Instances_SAT,
  "gpusat_incidence-vs-dynasp-Width_16-20.png",
  "gpusat incidence",
  "dynasp incidence",
  "dynqbf",
  "sharpSAT"
)

```

## gpusat vs. dynasp vs dynqbf vs. sharpSAT SAT: Width 21-25

```{r gpusat vs. dynasp vs dynqbf vs. sharpSAT SAT: Width 21-25, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT primal: Width 21-25",
  Results$setting == "primal_double_w-14_m-24" &
    Results$instance %in% Instances_Primal_Width_21_25 &
    Results$instance %in% Instances_SAT,
  Results$setting == "dynasp_primal" &
    Results$instance %in% Instances_Primal_Width_21_25 &
    Results$instance %in% Instances_SAT,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Primal_Width_21_25 &
    Results$instance %in% Instances_SAT,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Primal_Width_21_25 &
    Results$instance %in% Instances_SAT,
  "gpusat_primal-vs-dynasp-Width_21-25.png",
  "gpusat primal",
  "dynasp primal",
  "dynqbf",
  "sharpSAT"
)

generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT incidence: Width 21-25",
  Results$setting == "incidence_double_w-14_m-24" &
    Results$instance %in% Instances_Incidence_Width_21_25 &
    Results$instance %in% Instances_SAT,
  Results$setting == "dynasp_incidence" &
    Results$instance %in% Instances_Incidence_Width_21_25 &
    Results$instance %in% Instances_SAT,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Incidence_Width_21_25 &
    Results$instance %in% Instances_SAT,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Incidence_Width_21_25 &
    Results$instance %in% Instances_SAT,
  "gpusat_incidence-vs-dynasp-Width_21-25.png",
  "gpusat incidence",
  "dynasp incidence",
  "dynqbf",
  "sharpSAT"
)

```

## gpusat vs. dynasp vs dynqbf vs. sharpSAT SAT: Width 26-30

```{r gpusat vs. dynasp vs dynqbf vs. sharpSAT SAT: Width 26-30, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT primal: Width 26-30",
  Results$setting == "primal_double_w-14_m-24" &
    Results$instance %in% Instances_Primal_Width_26_30 &
    Results$instance %in% Instances_SAT,
  Results$setting == "dynasp_primal" &
    Results$instance %in% Instances_Primal_Width_26_30 &
    Results$instance %in% Instances_SAT,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Primal_Width_26_30 &
    Results$instance %in% Instances_SAT,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Primal_Width_26_30 &
    Results$instance %in% Instances_SAT,
  "gpusat_primal-vs-dynasp-Width_26-30.png",
  "gpusat primal",
  "dynasp primal",
  "dynqbf",
  "sharpSAT"
)

generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT incidence: Width 26-30",
  Results$setting == "incidence_double_w-14_m-24" &
    Results$instance %in% Instances_Incidence_Width_26_30 &
    Results$instance %in% Instances_SAT,
  Results$setting == "dynasp_incidence" &
    Results$instance %in% Instances_Incidence_Width_26_30 &
    Results$instance %in% Instances_SAT,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Incidence_Width_26_30 &
    Results$instance %in% Instances_SAT,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Incidence_Width_26_30 &
    Results$instance %in% Instances_SAT,
  "gpusat_incidence-vs-dynasp-Width_26-30.png",
  "gpusat incidence",
  "dynasp incidence",
  "dynqbf",
  "sharpSAT"
)

```

## gpusat vs. dynasp vs dynqbf vs. sharpSAT SAT: Width 31-40

```{r gpusat vs. dynasp vs dynqbf vs. sharpSAT SAT: Width 31-40, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT primal: Width 31-40",
  Results$setting == "primal_double_w-14_m-24" &
    Results$instance %in% Instances_Primal_Width_31_40 &
    Results$instance %in% Instances_SAT,
  Results$setting == "dynasp_primal" &
    Results$instance %in% Instances_Primal_Width_31_40 &
    Results$instance %in% Instances_SAT,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Primal_Width_31_40 &
    Results$instance %in% Instances_SAT,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Primal_Width_31_40 &
    Results$instance %in% Instances_SAT,
  "gpusat_primal-vs-dynasp-Width_31-40.png",
  "gpusat primal",
  "dynasp primal",
  "dynqbf",
  "sharpSAT"
)

generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT incidence: Width 31-40",
  Results$setting == "incidence_double_w-14_m-24" &
    Results$instance %in% Instances_Incidence_Width_31_40 &
    Results$instance %in% Instances_SAT,
  Results$setting == "dynasp_incidence" &
    Results$instance %in% Instances_Incidence_Width_31_40 &
    Results$instance %in% Instances_SAT,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Incidence_Width_31_40 &
    Results$instance %in% Instances_SAT,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Incidence_Width_31_40 &
    Results$instance %in% Instances_SAT,
  "gpusat_incidence-vs-dynasp-Width_31-40.png",
  "gpusat incidence",
  "dynasp incidence",
  "dynqbf",
  "sharpSAT"
)

```

## gpusat vs. dynasp vs dynqbf vs. sharpSAT UNSAT: Width 1-15

```{r gpusat vs. dynasp vs dynqbf vs. sharpSAT UNSAT: Width 1-15, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT primal: Width 1-15",
  Results$setting == "primal_double_w-14_m-24" &
    Results$instance %in% Instances_Primal_Width_1_15 &
    Results$instance %in% Instances_UNSAT,
  Results$setting == "dynasp_primal" &
    Results$instance %in% Instances_Primal_Width_1_15 &
    Results$instance %in% Instances_UNSAT,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Primal_Width_1_15 &
    Results$instance %in% Instances_UNSAT,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Primal_Width_1_15 &
    Results$instance %in% Instances_UNSAT,
  "gpusat_primal-vs-dynasp-Width_1-15.png",
  "gpusat primal",
  "dynasp primal",
  "dynqbf",
  "sharpSAT"
)

generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT incidence: Width 1-15",
  Results$setting == "incidence_double_w-14_m-24" &
    Results$instance %in% Instances_Incidence_Width_1_15 &
    Results$instance %in% Instances_UNSAT,
  Results$setting == "dynasp_incidence" &
    Results$instance %in% Instances_Incidence_Width_1_15 &
    Results$instance %in% Instances_UNSAT,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Incidence_Width_1_15 &
    Results$instance %in% Instances_UNSAT,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Incidence_Width_1_15 &
    Results$instance %in% Instances_UNSAT,
  "gpusat_incidence-vs-dynasp-Width_1-15.png",
  "gpusat incidence",
  "dynasp incidence",
  "dynqbf",
  "sharpSAT"
)

```

## gpusat vs. dynasp vs dynqbf vs. sharpSAT UNSAT: Width 16-20

```{r gpusat vs. dynasp vs dynqbf vs. sharpSAT UNSAT: Width 16-20, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT primal: Width 16-20",
  Results$setting == "primal_double_w-14_m-24" &
    Results$instance %in% Instances_Primal_Width_16_20 &
    Results$instance %in% Instances_UNSAT,
  Results$setting == "dynasp_primal" &
    Results$instance %in% Instances_Primal_Width_16_20 &
    Results$instance %in% Instances_UNSAT,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Primal_Width_16_20 &
    Results$instance %in% Instances_UNSAT,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Primal_Width_16_20 &
    Results$instance %in% Instances_UNSAT,
  "gpusat_primal-vs-dynasp-Width_16-20.png",
  "gpusat primal",
  "dynasp primal",
  "dynqbf",
  "sharpSAT"
)

generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT incidence: Width 16-20",
  Results$setting == "incidence_double_w-14_m-24" &
    Results$instance %in% Instances_Incidence_Width_16_20 &
    Results$instance %in% Instances_UNSAT,
  Results$setting == "dynasp_incidence" &
    Results$instance %in% Instances_Incidence_Width_16_20 &
    Results$instance %in% Instances_UNSAT,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Incidence_Width_16_20 &
    Results$instance %in% Instances_UNSAT,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Incidence_Width_16_20 &
    Results$instance %in% Instances_UNSAT,
  "gpusat_incidence-vs-dynasp-Width_16-20.png",
  "gpusat incidence",
  "dynasp incidence",
  "dynqbf",
  "sharpSAT"
)

```

## gpusat vs. dynasp vs dynqbf vs. sharpSAT UNSAT: Width 21-25

```{r gpusat vs. dynasp vs dynqbf vs. sharpSAT UNSAT: Width 21-25, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT primal: Width 21-25",
  Results$setting == "primal_double_w-14_m-24" &
    Results$instance %in% Instances_Primal_Width_21_25 &
    Results$instance %in% Instances_UNSAT,
  Results$setting == "dynasp_primal" &
    Results$instance %in% Instances_Primal_Width_21_25 &
    Results$instance %in% Instances_UNSAT,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Primal_Width_21_25 &
    Results$instance %in% Instances_UNSAT,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Primal_Width_21_25 &
    Results$instance %in% Instances_UNSAT,
  "gpusat_primal-vs-dynasp-Width_21-25.png",
  "gpusat primal",
  "dynasp primal",
  "dynqbf",
  "sharpSAT"
)

generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT incidence: Width 21-25",
  Results$setting == "incidence_double_w-14_m-24" &
    Results$instance %in% Instances_Incidence_Width_21_25 &
    Results$instance %in% Instances_UNSAT,
  Results$setting == "dynasp_incidence" &
    Results$instance %in% Instances_Incidence_Width_21_25 &
    Results$instance %in% Instances_UNSAT,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Incidence_Width_21_25 &
    Results$instance %in% Instances_UNSAT,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Incidence_Width_21_25 &
    Results$instance %in% Instances_UNSAT,
  "gpusat_incidence-vs-dynasp-Width_21-25.png",
  "gpusat incidence",
  "dynasp incidence",
  "dynqbf",
  "sharpSAT"
)

```

## gpusat vs. dynasp vs dynqbf vs. sharpSAT UNSAT: Width 26-30

```{r gpusat vs. dynasp vs dynqbf vs. sharpSAT UNSAT: Width 26-30, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT primal: Width 26-30",
  Results$setting == "primal_double_w-14_m-24" &
    Results$instance %in% Instances_Primal_Width_26_30 &
    Results$instance %in% Instances_UNSAT,
  Results$setting == "dynasp_primal" &
    Results$instance %in% Instances_Primal_Width_26_30 &
    Results$instance %in% Instances_UNSAT,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Primal_Width_26_30 &
    Results$instance %in% Instances_UNSAT,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Primal_Width_26_30 &
    Results$instance %in% Instances_UNSAT,
  "gpusat_primal-vs-dynasp-Width_26-30.png",
  "gpusat primal",
  "dynasp primal",
  "dynqbf",
  "sharpSAT"
)

generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT incidence: Width 26-30",
  Results$setting == "incidence_double_w-14_m-24" &
    Results$instance %in% Instances_Incidence_Width_26_30 &
    Results$instance %in% Instances_UNSAT,
  Results$setting == "dynasp_incidence" &
    Results$instance %in% Instances_Incidence_Width_26_30 &
    Results$instance %in% Instances_UNSAT,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Incidence_Width_26_30 &
    Results$instance %in% Instances_UNSAT,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Incidence_Width_26_30 &
    Results$instance %in% Instances_UNSAT,
  "gpusat_incidence-vs-dynasp-Width_26-30.png",
  "gpusat incidence",
  "dynasp incidence",
  "dynqbf",
  "sharpSAT"
)

```

## gpusat vs. dynasp vs dynqbf vs. sharpSAT UNSAT: Width 31-40

```{r gpusat vs. dynasp vs dynqbf vs. sharpSAT UNSAT: Width 31-40, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT primal: Width 31-40",
  Results$setting == "primal_double_w-14_m-24" &
    Results$instance %in% Instances_Primal_Width_31_40 &
    Results$instance %in% Instances_UNSAT,
  Results$setting == "dynasp_primal" &
    Results$instance %in% Instances_Primal_Width_31_40 &
    Results$instance %in% Instances_UNSAT,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Primal_Width_31_40 &
    Results$instance %in% Instances_UNSAT,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Primal_Width_31_40 &
    Results$instance %in% Instances_UNSAT,
  "gpusat_primal-vs-dynasp-Width_31-40.png",
  "gpusat primal",
  "dynasp primal",
  "dynqbf",
  "sharpSAT"
)

generateInstanceKaktusPlot4(
  "gpusat vs. dynasp vs dynqbf vs. sharpSAT incidence: Width 31-40",
  Results$setting == "incidence_double_w-14_m-24" &
    Results$instance %in% Instances_Incidence_Width_31_40 &
    Results$instance %in% Instances_UNSAT,
  Results$setting == "dynasp_incidence" &
    Results$instance %in% Instances_Incidence_Width_31_40 &
    Results$instance %in% Instances_UNSAT,
  Results$setting == "dynqbf_all_s1234" &
    Results$instance %in% Instances_Incidence_Width_31_40 &
    Results$instance %in% Instances_UNSAT,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Incidence_Width_31_40 &
    Results$instance %in% Instances_UNSAT,
  "gpusat_incidence-vs-dynasp-Width_31-40.png",
  "gpusat incidence",
  "dynasp incidence",
  "dynqbf",
  "sharpSAT"
)

```

## gpusat vs. dynasp

```{r UNSAT gpusat vs. dynasp, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
generateInstanceKaktusPlot(
  "gpusat vs. dynasp primal Width 30",
  Results$setting == "primal_double_w-14_m-24" &
    Results$instance %in% Instances_Primal_Width_30,
  Results$setting == "dynasp_primal" &
    Results$instance %in% Instances_Primal_Width_30,
  "gpusat_primal-vs-dynasp-Width_30.png",
  "gpusat primal",
  "dynasp primal"
)

generateInstanceKaktusPlot(
  "gpusat vs. dynasp incidence Width 30",
  Results$setting == "incidence_double_w-14_m-24" &
    Results$instance %in% Instances_Incidence_Width_30,
  Results$setting == "dynasp_incidence" &
    Results$instance %in% Instances_Incidence_Width_30,
  "gpusat_incidence-vs-dynasp-Width_30.png",
  "gpusat incidence",
  "dynasp incidence"
)

```

## dynasp vs. sharpsat

```{r dynasp vs. sharpSAT, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
generateInstanceKaktusPlot(
  "dynasp vs. sharpsat",
  Results$setting == "dynasp_primal" &
    Results$instance %in% Instances_Primal_Width_30,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Primal_Width_30,
  "dynasp_primal-vs-sharpsat.png",
  "dynasp primal",
  "sharpsat"
)

generateInstanceKaktusPlot(
  "dynasp vs. sharpsat",
  Results$setting == "dynasp_incidence" &
    Results$instance %in% Instances_Incidence_Width_30,
  Results$solver == "sharpSAT" &
    Results$instance %in% Instances_Incidence_Width_30,
  "dynasp_incidence-vs-sharpsat.png",
  "dynasp incidence",
  "sharpsat"
)

```

## gpusat vs. dynasp: Solutions more than 5000 width <= 30

```{r gpusat vs. dynasp: Solutions more than 5000, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
generateInstanceKaktusPlot(
  "gpusat vs. dynasp primal models > 5000",
  Results$setting == "primal_double_w-14_m-24" &
    Results$instance %in% Instances_Primal_Width_30 &
    Results$instance %in% Instances_Models_5000_p,
  Results$setting == "dynasp_primal" &
    Results$instance %in% Instances_Primal_Width_30 &
    Results$instance %in% Instances_Models_5000_p,
  "gpusat_primal-vs-dynasp-models_g_5000.png",
  "gpusat primal",
  "dynasp primal"
)

generateInstanceKaktusPlot(
  "gpusat vs. dynasp incidence models > 5000",
  Results$setting == "incidence_double_w-14_m-24" &
    Results$instance %in% Instances_Incidence_Width_30 &
    Results$instance %in% Instances_Models_5000_p,
  Results$setting == "dynasp_incidence" &
    Results$instance %in% Instances_Incidence_Width_30 &
    Results$instance %in% Instances_Models_5000_p,
  "gpusat_incidence-vs-dynasp-models_g_5000.png",
  "gpusat incidence",
  "dynasp incidence"
)

```

## gpusat vs. dynasp: Solutions less than 5000 width <= 30

```{r gpusat vs. dynasp: Solutions less than 5000, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
generateInstanceKaktusPlot(
  "gpusat vs. dynasp primal models <= 5000",
  Results$setting == "primal_double_w-14_m-24" &
    Results$instance %in% Instances_Primal_Width_30 &
    Results$instance %in% Instances_Models_5000,
  Results$setting == "dynasp_primal" &
    Results$instance %in% Instances_Primal_Width_30 &
    Results$instance %in% Instances_Models_5000,
  "gpusat_primal-vs-dynasp-models_l_5000.png",
  "gpusat primal",
  "dynasp primal"
)

generateInstanceKaktusPlot(
  "gpusat vs. dynasp incidence models <= 5000",
  Results$setting == "incidence_double_w-14_m-24" &
    Results$instance %in% Instances_Incidence_Width_30 &
    Results$instance %in% Instances_Models_5000,
  Results$setting == "dynasp_incidence" &
    Results$instance %in% Instances_Incidence_Width_30 &
    Results$instance %in% Instances_Models_5000,
  "gpusat_incidence-vs-dynasp-models_l_5000.png",
  "gpusat incidence",
  "dynasp incidence"
)

```

